---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---



```{r}
library(magrittr)
library(dplyr)

```


```{r}
data_dir <- "/Users/benjaminsmith/Dropbox (University of Oregon)/UO-SAN Lab/Berkman Lab/Devaluation/analysis_files/data/"

preprocessed_data_filepath <- paste0(data_dir,"cloudresearch_survey_results/orfcs_preprocessed_anon_by_subj.csv")
library(readr)
library(ggplot2)
library(GGally)
preprocessed_data_raw <- readr::read_csv(preprocessed_data_filepath)


```

A few preprocessed data points:

## Data quality check

So the reverse score items are still reversescored in our EDM_reversescored. What is suspicious are subjects who score highly in forwardscore an low in reversescore, particularly if they're round numbers.





```{r}
ggplot(preprocessed_data_raw,aes(EDM_forwardscore,EDM_reversescored))+geom_point(alpha=0.1)
```

```{r}
#table(preprocessed_data$EDM_forwardscore,preprocessed_data$EDM_reversescored)
```


OK, there are 3 subjects with high reversescored items and low forwardscored items and are clear outliers we can delete. Should probably follow up this process with a more scientific outlier detection mechanism but this will do for now.


```{r}
rows_to_remove <- ((preprocessed_data_raw$EDM_forwardscore<2 & preprocessed_data_raw$EDM_reversescored>4) |
  (preprocessed_data_raw$EDM_forwardscore>=4.5 & preprocessed_data_raw$EDM_reversescored<2))
rows_to_remove[is.na(rows_to_remove)]<-FALSE
sum(rows_to_remove)
sub_ids_to_remove <- preprocessed_data_raw[rows_to_remove,"SID"]
preprocessed_data <- preprocessed_data_raw %>% filter((SID %in% unlist(sub_ids_to_remove))==FALSE)
```
```{r}

preprocessed_data$DEMO_Age_c <- preprocessed_data$DEMO_Age-38 #using U.S. median age

preprocessed_data$RaceCategorical<-factor(preprocessed_data$RaceCategorical,levels=unique(preprocessed_data$RaceCategorical))

preprocessed_data$RuralZIP_i <- as.numeric(preprocessed_data$RuralZIP)
preprocessed_data$RaceCategorical2 <- as.character(preprocessed_data$RaceCategorical)
preprocessed_data$RaceCategorical2[preprocessed_data$RaceCategorical2=="RaceNotReported"] <- "OtherRaceRaceNotReported"
preprocessed_data$RaceCategorical2[preprocessed_data$RaceCategorical2=="OtherRace"] <- "OtherRaceRaceNotReported"
preprocessed_data$RaceCategorical2 <-factor(preprocessed_data$RaceCategorical2,levels=names(sort(table(preprocessed_data$RaceCategorical2),decreasing=TRUE)))
```

## Description


reference for the analysis plan is at: https://osf.io/k7jav

From the analysis plan:

> People in more safer community environments and communities with healthier food environments (a) will have better eating behavior and (b) will be in better health, after controlling for perceived stress.

Let's take a look at our distribution of eating behavior and health.

First, health outcome, as measured by BMI:

```{r}
ggplot(preprocessed_data,aes(WEIGHT, BMI))+geom_point()+labs(title="pre-clean")


#need to remove this one data point for data quality issue.
preprocessed_data[!is.na(preprocessed_data$WEIGHT) & preprocessed_data$WEIGHT>500,c("WEIGHT","WEIGHT_kg","BMI")] <- NA

ggplot(preprocessed_data,aes(WEIGHT, BMI))+geom_point()+labs(title="post-clean")
```



And health:
```{r}

summary(lm(BMI~FFQ_cancer_promoting+FFQ_cancer_preventing+DEMO_Age, preprocessed_data))
```

```{r}
#gender differences STRONGLY significant.
summary(lm(BMI~FFQ_cancer_promoting*Gender3C+FFQ_cancer_preventing*Gender3C+DEMO_Age, preprocessed_data%>% filter(Gender3C %in% c("Male", "Female"))))


summary(lm(BMI~FFQ_cancer_promoting+FFQ_cancer_preventing+DEMO_Age, preprocessed_data %>% filter(Gender3C=="Male")))
summary(lm(BMI~FFQ_cancer_promoting+FFQ_cancer_preventing+DEMO_Age, preprocessed_data %>% filter(Gender3C=="Female")))

#try with a Sex-controlled or categorical 
```


```{r}

ggplot(preprocessed_data %>% filter(Gender3C %in% c("Male", "Female")),
       aes(FFQ_cancer_promoting,BMI,color=Gender3C,group=Gender3C))+geom_point(alpha=0.5)+ geom_smooth(method="lm", formula=y~x,aes(group=Gender3C))
```


```{r}
ggplot(preprocessed_data %>% filter(Gender3C %in% c("Male", "Female")),
       aes(FFQ_cancer_preventing,BMI,color=Gender3C,group=Gender3C))+geom_point(alpha=0.5)+ geom_smooth(method="lm", formula=y~x,aes(group=Gender3C))
```



```{r}

hist(preprocessed_data$cancer_promoting_minus_preventing_FFQ,breaks = 20)

hist(preprocessed_data$FFQ_cancer_promoting,breaks = 20)

#let's create a log measure of this because it is right-skewed
#though perhaps the danger is right-skewed as well? so I'm not sure.
preprocessed_data$FFQ_cancer_promoting_log <- log(preprocessed_data$FFQ_cancer_promoting)
preprocessed_data$FFQ_cancer_preventing_log <- log(preprocessed_data$FFQ_cancer_preventing)

hist(preprocessed_data$FFQ_cancer_promoting_log,breaks = 20)


ggplot(preprocessed_data,aes(FFQ_cancer_promoting, BMI))+geom_point()+labs(title="post-clean")
ggplot(preprocessed_data,aes(cancer_promoting_minus_preventing_FFQ, BMI))+geom_point()+labs(title="post-clean")
ggplot(preprocessed_data,aes(FFQ_cancer_preventing_log, BMI))+geom_point()+labs(title="post-clean")

cor.test(preprocessed_data$cancer_promoting_minus_preventing_FFQ,preprocessed_data$BMI)

cor.test(preprocessed_data$FFQ_cancer_promoting,preprocessed_data$BMI)
cor.test(preprocessed_data$FFQ_cancer_preventing,preprocessed_data$BMI)
cor.test(preprocessed_data$FFQ_cancer_preventing_log,preprocessed_data$BMI)

```

```{r }

custom_points <- function(...){
  ggally_points(...,alpha=0.2)
}
```

```{r eval=FALSE, fig.height=14, fig.width=14, include=FALSE}
ggpairs(preprocessed_data[c("BMI",colnames(preprocessed_data)[grepl("FFQ",colnames(preprocessed_data))])]
        ,progress=FALSE
        ,lower = list(continuous = custom_points)
        )
```


We should use cancer_preventing as our health behavior--it seems to relate most closely with BMI. That was a bit of a suprise but there you go!

Also--how many of the subcategories of cancer_promoting should we be looking at?


Now let's look at perceived stress

```{r}
hist(preprocessed_data$PSS_sum,breaks=30)
```

OK, now we look at the harder items: community safety and food access.


For food access, and community safety we have MESA:

```{r}
#library("ggpairs")
pairs(preprocessed_data[c("MESA_freshproduce","MESA_healthyfoodavailability","MESA_lowfat","MESA_mean","MESA_safetyfromcrime", "MESA_neighborhoodconnectedness")])
```





> To measure the effect of community on eating behavior and health, we will use two linear models to predict (1) eating behavior and (2) health outcome from

> (a) Community healthy food environment

> (b) Community safety

> (c) self-report confounding variables PSS-4

> (d) demographic confounders relating to age and race



OK great, so now we have the ability to to all of that 


```{r}
#need to tidy race a bit.

predict_bmi <- lm(BMI~
                    MESA_healthyfoodavailability+MESA_safetyfromcrime+PSS_sum+
                    DEMO_Age+Gender3C+RaceCategorical,
                  preprocessed_data)
summary(predict_bmi)
```



#### Methodological refinement

```{r}
#need to tidy race a bit.

predict_bmi <- lm(BMI~
                    MESA_healthyfoodavailability+MESA_safetyfromcrime+PSS_sum+
                    DEMO_Age+I(DEMO_Age^2)+Gender3C+RaceCategorical,
                  preprocessed_data)
summary(predict_bmi)
```

#### Skewness
```{r}
#install.packages("moments")
library(moments)
```

```{r}
lapply(c("BMI","cancer_promoting_minus_preventing_FFQ","MESA_healthyfoodavailability","MESA_safetyfromcrime","PSS_sum"),
       function(label){
  data_vec <- preprocessed_data[[label]]
  print(label)
  print(paste(skewness(data_vec,na.rm=TRUE),skewness(log(data_vec),na.rm=TRUE),skewness(1-log((max(data_vec,na.rm=TRUE)+1)-data_vec),na.rm=TRUE)))
  print(shapiro.test(data_vec))
  
  hist(data_vec,main=label)
       }
)
```

```{r}
hist(preprocessed_data$MESA_healthyfoodavailability)
hist(log(preprocessed_data$MESA_healthyfoodavailability))
hist(log(6)-log(6-preprocessed_data$MESA_healthyfoodavailability))
```
```{r}
preprocessed_data$neg_ln_MESA_healthyfoodavailability <- log(6) - log(6-preprocessed_data$MESA_healthyfoodavailability)
preprocessed_data$ln_BMI <- log(preprocessed_data$BMI)
predict_bmi <- lm(ln_BMI~
                    neg_ln_MESA_healthyfoodavailability+MESA_safetyfromcrime+PSS_sum+
                    DEMO_Age+I(DEMO_Age^2)+Gender3C+RaceCategorical,
                  preprocessed_data)
summary(predict_bmi)

```


#### population subgroup

```{r}
predict_bmi_25p <- lm(BMI~
                    MESA_healthyfoodavailability+MESA_safetyfromcrime+PSS_sum+
                    DEMO_Age+Gender3C+RaceCategorical,
                  preprocessed_data %>% filter(BMI>25))
summary(predict_bmi_25p)
```



```{r}
predict_bmi_25p <- lm(BMI~
                    MESA_healthyfoodavailability+MESA_safetyfromcrime+PSS_sum+
                    DEMO_Age+I(DEMO_Age^2)+Gender3C+RaceCategorical,
                  preprocessed_data %>% filter(BMI>25))
summary(predict_bmi_25p)
```


```{r}
predict_bmi_quad <- lm(BMI~
                    MESA_healthyfoodavailability+I(MESA_healthyfoodavailability^2)+MESA_safetyfromcrime+PSS_sum+
                    DEMO_Age+Gender3C+RaceCategorical,
                  preprocessed_data)
summary(predict_bmi_quad)
```

```{r}
ggplot(preprocessed_data,aes(MESA_healthyfoodavailability,BMI))+
  geom_smooth(method = "lm")+
  geom_point(alpha=0.2)
```



```{r}
predict_ffq <- lm(cancer_promoting_minus_preventing_FFQ~
                    MESA_healthyfoodavailability+MESA_safetyfromcrime+PSS_sum+
                    DEMO_Age+Gender3C+RaceCategorical,
                  preprocessed_data)
summary(predict_ffq)
```


```{r}
predict_ffq <- lm(cancer_promoting_minus_preventing_FFQ~
                    MESA_healthyfoodavailability+MESA_safetyfromcrime+PSS_sum+
                    DEMO_Age+I(DEMO_Age^2)+Gender3C+RaceCategorical,
                  preprocessed_data)
summary(predict_ffq)
```


```{r}
ggplot(preprocessed_data,aes(MESA_healthyfoodavailability,cancer_promoting_minus_preventing_FFQ))+
  geom_smooth(method = "lm")+
  geom_point(alpha=0.2)
```


```{r}
predict_ffq_women <- lm(cancer_promoting_minus_preventing_FFQ~
                    MESA_healthyfoodavailability+MESA_safetyfromcrime+PSS_sum+
                    DEMO_Age+RaceCategorical,
                  preprocessed_data %>% filter(Gender3C=="Female"))

summary(predict_ffq_women)
```

> There is a rural-urban disparity in (a) eating behavior and (b) health outcomes in Oregon, after controlling for age and race but not income or SES.

```{r}
predict_ffq_rural <- lm(cancer_promoting_minus_preventing_FFQ~RuralZIP+
                    #MESA_healthyfoodavailability+MESA_safetyfromcrime+PSS_sum+
                    DEMO_Age+Gender+RaceCategorical,
                  preprocessed_data)
summary(predict_ffq_rural)
```
```{r}
predict_bmi_rural <- lm(BMI~RuralZIP+
                    #MESA_healthyfoodavailability+MESA_safetyfromcrime+PSS_sum+
                    DEMO_Age+Gender3C+RaceCategorical,
                  preprocessed_data)
summary(predict_bmi_rural)
```

```{r}
ggplot(preprocessed_data %>% filter(!is.na(RuralZIP)),aes(x=RuralZIP==TRUE,y=BMI))+geom_jitter(alpha=0.5)+geom_boxplot(fill=NA)
```



> The rural-urban disparity can be partially explained by the availability of healthy food in the community.


```{r}
predict_bmi_rural_2 <- lm(BMI~RuralZIP+
                    MESA_healthyfoodavailability+
                    DEMO_Age+Gender+RaceCategorical,
                  preprocessed_data)
summary(predict_bmi_rural_2)
```
Need to follow this up with a full mediation model.


```{r}
hist(preprocessed_data$MESA_healthyfoodavailability,breaks=30)
print(sort(preprocessed_data$MESA_healthyfoodavailability))
```
Distribution of values suggests a bias towards always answering "strongly agree" or always answering "agree".

Wonder how they correlate with the next item on the scale, which is the eating disregulation measure.

```{r}
ggplot(preprocessed_data,aes(MESA_healthyfoodavailability,EDM_mean))+geom_point(alpha=0.02)
```
There are a large number of responses giving either 3, 4, or 5. Wonder if there is any principled way to remove them as they look like lazy responses and noise.

```{r}
#https://www.rdocumentation.org/packages/mediation/versions/4.5.0/topics/mediate
library(mediation)
#first need to only get rows that are NA on all the values; need to do this prior because we have two different models and need them using the same rows.
#strictly speaking, only need to add columns not included in both; lm package will consistently eliminate the rest.
exclude_row <- rowSums(is.na(preprocessed_data[,c("BMI","MESA_healthyfoodavailability")]))>0

preprocessed_data$MESA_healthyfoodavailability_ln <- log(preprocessed_data$MESA_healthyfoodavailability)
predict_mediator <- lm(MESA_healthyfoodavailability~RuralZIP+DEMO_Age+Gender3C+RaceCategorical,preprocessed_data[!exclude_row,])
predict_outcome <- lm(BMI~MESA_healthyfoodavailability+RuralZIP+DEMO_Age+Gender3C+RaceCategorical,preprocessed_data[!exclude_row,])

healthy_food_mediation <- mediate(predict_mediator,predict_outcome,boot=FALSE,sims=2000,treat="RuralZIP",mediator="MESA_healthyfoodavailability")

```


We didn't pre-register taking the log of MESA_healthyfood availability, but it is a reasonable deviation considering its non-normality.

```{r}
summary(healthy_food_mediation)
```

The mediation effect is not quite significant. Disappointing!

```{r}
plot(healthy_food_mediation)
```


How about just in women, though?


```{r}
predict_bmi_rural_female <- lm(BMI~RuralZIP+
                    #MESA_healthyfoodavailability+MESA_safetyfromcrime+PSS_sum+
                    DEMO_Age+RaceCategorical,
                  preprocessed_data %>% filter(Gender3C=="Female"))
summary(predict_bmi_rural_female)

predict_bmi_rural_2_female <- lm(BMI~RuralZIP+
                    MESA_healthyfoodavailability+
                    DEMO_Age+RaceCategorical,
                  preprocessed_data %>% filter(Gender3C=="Female"))
summary(predict_bmi_rural_2_female)
```


```{r}
#https://www.rdocumentation.org/packages/mediation/versions/4.5.0/topics/mediate
library(mediation)
#first need to only get rows that are NA on all the values; need to do this prior because we have two different models and need them using the same rows.
#strictly speaking, only need to add columns not included in both; lm package will consistently eliminate the rest.
exclude_row <- rowSums(is.na(preprocessed_data[,c("BMI","MESA_healthyfoodavailability")]))>0

preprocessed_data$MESA_healthyfoodavailability_ln <- log(preprocessed_data$MESA_healthyfoodavailability)
predict_mediator <- lm(MESA_healthyfoodavailability~RuralZIP+DEMO_Age+RaceCategorical,(preprocessed_data[!exclude_row,] %>% filter(Gender3C=="Female")))
predict_outcome <- lm(BMI~MESA_healthyfoodavailability+RuralZIP+DEMO_Age+RaceCategorical,(preprocessed_data[!exclude_row,] %>% filter(Gender3C=="Female")))

healthy_food_mediation <- mediate(predict_mediator,predict_outcome,boot=FALSE,sims=2000,treat="RuralZIP",mediator="MESA_healthyfoodavailability")

```

```{r}
summary(healthy_food_mediation)
```



hmm, we actuallly don't detect an effect of healthy food availability for women only, but this may be down to power



```{r}
#https://www.rdocumentation.org/packages/mediation/versions/4.5.0/topics/mediate
library(mediation)
#first need to only get rows that are NA on all the values; need to do this prior because we have two different models and need them using the same rows.
#strictly speaking, only need to add columns not included in both; lm package will consistently eliminate the rest.
exclude_row <- rowSums(is.na(preprocessed_data[,c("BMI","MESA_healthyfoodavailability")]))>0

preprocessed_data$MESA_healthyfoodavailability_ln <- log(preprocessed_data$MESA_healthyfoodavailability)
predict_mediator <- lm(MESA_healthyfoodavailability~RuralZIP+DEMO_Age+RaceCategorical,(preprocessed_data[!exclude_row,] %>% filter(Gender3C=="Male")))
predict_outcome <- lm(BMI~MESA_healthyfoodavailability+RuralZIP+DEMO_Age+RaceCategorical,(preprocessed_data[!exclude_row,] %>% filter(Gender3C=="Male")))

healthy_food_mediation <- mediate(predict_mediator,predict_outcome,boot=FALSE,sims=2000,treat="RuralZIP",mediator="MESA_healthyfoodavailability")

```

```{r}
summary(healthy_food_mediation)
```

```{r}
predict_ffq_rural_female <- lm(cancer_promoting_minus_preventing_FFQ~RuralZIP+
                    #MESA_healthyfoodavailability+MESA_safetyfromcrime+PSS_sum+
                    DEMO_Age+RaceCategorical,
                  preprocessed_data %>% filter(Gender3C=="Female"))
summary(predict_ffq_rural_female)

predict_ffq_rural_2_female <- lm(cancer_promoting_minus_preventing_FFQ~RuralZIP+
                    MESA_healthyfoodavailability+
                    DEMO_Age+RaceCategorical,
                  preprocessed_data %>% filter(Gender3C=="Female"))
summary(predict_ffq_rural_2_female)
```





> Eating behavior and health outcomes will be influenced by perceived stress (negatively), the Self Report Habit Index (negatively). Health outcomes will be influenced by the short version of the IPAQ (negatively)



```{r}
predict_health_outcomes <- lm(BMI~PSS_sum+SRHI_healthy+SRHI_unhealthy+IPAQ_total_METminutes+Gender3C + IPAQ_sittinghours,
                  preprocessed_data)
summary(predict_health_outcomes)
```

```{r}
predict_eating_behavior <- lm(cancer_promoting_minus_preventing_FFQ~PSS_sum+SRHI_healthy+SRHI_unhealthy+IPAQ_total_METminutes+Gender3C,
                  preprocessed_data)
summary(predict_eating_behavior)
```

~~Contrary to prediction, IPAQ predicts FFQ but NOT BMI. Suggests a cultural link `health-concerned' people who work out more and eat more vegetables _despite_ their lack of efficacy??? Or just social class or something.~~

## Firming up that initial finding--does FFQ mediate that relationship between community health and BMI?


```{r}
library(mediation)

data_to_measure <- preprocessed_data %>% filter(!is.na(BMI) & Gender3C %in% c("Female","Male"))

#mediator   cancer_promoting_minus_preventing_FFQ
#treatment  MESA_healthyfoodavailability


mb <- lm(cancer_promoting_minus_preventing_FFQ~MESA_healthyfoodavailability+Gender3C+DEMO_Age_c+I(DEMO_Age_c^2)+RaceCategorical2,data_to_measure)
mc <- lm(BMI~MESA_healthyfoodavailability+Gender3C+DEMO_Age_c+I(DEMO_Age_c^2)+RaceCategorical2+cancer_promoting_minus_preventing_FFQ,data_to_measure)

mediate_result <- mediate(mb,mc,boot=TRUE,sims=10000,treat="MESA_healthyfoodavailability",mediator="cancer_promoting_minus_preventing_FFQ")
summary(mediate_result)
summary(mc)

```

## General analysis of different FFQ items

```{r, fig.width=10}
colnames(preprocessed_data)[grepl("FFQ",colnames(preprocessed_data))]

ffq_subitems <- c(
  "FFQ_dairy",
  "FFQ_empty_calories",
  "FFQ_fried_food",
  "FFQ_fruits",
  "FFQ_grains",
  "FFQ_meat",
  "FFQ_processed_meats",
  "FFQ_protein",
  "FFQ_red_meat",
  "FFQ_soups",
  "FFQ_sugary_foods",
  "FFQ_vegetables"
)

corrplot::corrplot(cor(preprocessed_data[c("BMI",ffq_subitems)],
                       
                      use = "pairwise.complete.obs"
                       ),type="upper",diag=FALSE, tl.srt=45,method = "number")
```

```{r}
summary(lm(BMI~
               FFQ_dairy +
  FFQ_empty_calories +
  FFQ_fried_food +
  FFQ_fruits +
  FFQ_grains +
  FFQ_meat +
  FFQ_processed_meats +
  FFQ_protein +
  FFQ_red_meat +
  FFQ_soups +
  FFQ_sugary_foods +
  FFQ_vegetables+
    PSS_sum+DEMO_Age+I(DEMO_Age^2)+Gender3C+RaceCategorical,
  preprocessed_data
             ))
```

```{r}
summary(lm(BMI~
               FFQ_dairy +
  FFQ_empty_calories +
  FFQ_fried_food +
  FFQ_fruits +
  FFQ_grains +
  FFQ_meat +
  FFQ_processed_meats +
  #FFQ_protein +
  FFQ_red_meat +
  FFQ_soups +
  FFQ_sugary_foods +
  FFQ_vegetables+
    PSS_sum+DEMO_Age+I(DEMO_Age^2)+Gender3C+RaceCategorical,
  preprocessed_data
             ))

```

```{r}

summary(lm(BMI~
  #             FFQ_dairy +
  FFQ_empty_calories +
  FFQ_fried_food +
  FFQ_fruits +
  FFQ_grains +
  FFQ_meat +
  FFQ_processed_meats +
  #FFQ_protein +
  FFQ_red_meat +
  FFQ_soups +
  FFQ_sugary_foods +
  FFQ_vegetables+
    PSS_sum+DEMO_Age+I(DEMO_Age^2)+Gender3C+RaceCategorical,
  preprocessed_data
             ))
```


```{r}

summary(lm(BMI~
  #             FFQ_dairy +
  FFQ_empty_calories +
  FFQ_fried_food +
  FFQ_fruits +
  FFQ_grains +
  FFQ_meat +
  FFQ_processed_meats +
  #FFQ_protein +
  FFQ_red_meat +
  #FFQ_soups +
  FFQ_sugary_foods +
  FFQ_vegetables+
    PSS_sum+DEMO_Age+I(DEMO_Age^2)+Gender3C+RaceCategorical,
  preprocessed_data
             ))
```




```{r}

summary(lm(BMI~
  #             FFQ_dairy +
  FFQ_empty_calories +
  FFQ_fried_food +
  #FFQ_fruits +
  FFQ_grains +
  FFQ_meat +
  FFQ_processed_meats +
  #FFQ_protein +
  FFQ_red_meat +
  #FFQ_soups +
  FFQ_sugary_foods +
  #FFQ_vegetables+
    PSS_sum+DEMO_Age+I(DEMO_Age^2)+Gender3C+RaceCategorical,
  preprocessed_data
             ))
```



```{r}

summary(lm(BMI~
  #             FFQ_dairy +
  FFQ_empty_calories +
  FFQ_fried_food +
  #FFQ_fruits +
  FFQ_grains +
  FFQ_meat +
  FFQ_processed_meats +
  #FFQ_protein +
  #FFQ_red_meat +
  #FFQ_soups +
  FFQ_sugary_foods +
  #FFQ_vegetables+
    PSS_sum+DEMO_Age+I(DEMO_Age^2)+Gender3C+RaceCategorical,
  preprocessed_data
             ))
```


```{r}

summary(lm(BMI~
  #             FFQ_dairy +
  FFQ_empty_calories +
  #FFQ_fried_food +
  #FFQ_fruits +
  FFQ_grains +
  FFQ_meat +
  FFQ_processed_meats +
  #FFQ_protein +
  #FFQ_red_meat +
  #FFQ_soups +
  FFQ_sugary_foods +
  #FFQ_vegetables+
    PSS_sum+DEMO_Age+I(DEMO_Age^2)+Gender3C+RaceCategorical,
  preprocessed_data
             ))
```

```{r}

summary(lm(BMI~
  #             FFQ_dairy +
  #FFQ_empty_calories +
  #FFQ_fried_food +
  #FFQ_fruits +
  FFQ_grains +
  FFQ_meat +
  FFQ_processed_meats +
  #FFQ_protein +
  #FFQ_red_meat +
  #FFQ_soups +
  FFQ_sugary_foods +
  #FFQ_vegetables+
    PSS_sum+DEMO_Age+I(DEMO_Age^2)+Gender3C+RaceCategorical,
  preprocessed_data
             ))
```



```{r}

summary(lm(BMI~
  #             FFQ_dairy +
  #FFQ_empty_calories +
  #FFQ_fried_food +
  #FFQ_fruits +
  FFQ_grains +
  FFQ_meat +
  #FFQ_processed_meats +
  #FFQ_protein +
  #FFQ_red_meat +
  #FFQ_soups +
  FFQ_sugary_foods +
  #FFQ_vegetables+
    PSS_sum+DEMO_Age+I(DEMO_Age^2)+Gender3C+RaceCategorical,
  preprocessed_data
             ))
```

OK. WEll, weird that veggies and fruits didn't last. What if we brought them back?

```{r}

summary(lm(BMI~
  #             FFQ_dairy +
  #FFQ_empty_calories +
  #FFQ_fried_food +
  FFQ_fruits +
  FFQ_grains +
  FFQ_meat +
  #FFQ_processed_meats +
  #FFQ_protein +
  #FFQ_red_meat +
  #FFQ_soups +
  FFQ_sugary_foods +
  FFQ_vegetables+
    PSS_sum+DEMO_Age+I(DEMO_Age^2)+Gender3C+RaceCategorical,
  preprocessed_data
             ))
```