---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

```{r}

library(magrittr)
library(dplyr)

```


```{r}
data_dir <- "/Users/benjaminsmith/Dropbox (University of Oregon)/UO-SAN Lab/Berkman Lab/Devaluation/analysis_files/data/"

preprocessed_data_filepath <- paste0(data_dir,"cloudresearch_survey_results/orfcs_preprocessed_anon_by_subj.csv")
library(readr)
library(ggplot2)
library(GGally)
preprocessed_data_raw <- readr::read_csv(preprocessed_data_filepath)


```



```{r}
rows_to_remove <- ((preprocessed_data_raw$EDM_forwardscore<2 & preprocessed_data_raw$EDM_reversescored>4) |
  (preprocessed_data_raw$EDM_forwardscore>=4.5 & preprocessed_data_raw$EDM_reversescored<2))
rows_to_remove[is.na(rows_to_remove)]<-FALSE
sum(rows_to_remove)
sub_ids_to_remove <- preprocessed_data_raw[rows_to_remove,"SID"]
preprocessed_data <- preprocessed_data_raw %>% filter((SID %in% unlist(sub_ids_to_remove))==FALSE)

preprocessed_data[!is.na(preprocessed_data$WEIGHT) & preprocessed_data$WEIGHT>500,c("WEIGHT","WEIGHT_kg","BMI")] <- NA



preprocessed_data$RaceCategorical<-factor(preprocessed_data$RaceCategorical,levels=unique(preprocessed_data$RaceCategorical))
```


What more do we want to do?

 - think we've done the main checks on gender. 
 - Measure only BMI=25+ population in order to get something more comparable with DEV study results. Probably copy initial pre-reg and run for filter with BMI=25+. This might be helpful for gender.
 - Check: does food consumption mediate the relationship between rural status and higher BMI?
 - Run full model from spreadsheet, trying to maximally explain food consumption and BMI. Ideally, include FCI to predict FFQ, but hopefully be able to include environment as well
 - Contact Nick's lab about analyzing our detailed location data to get nearby shops
 - Run a small analysis on foods consumed to identify relationship between different food consumption patterns and BMI. But this hsould probably be done on DEV dataset.


```{r}
print(summary(lm(BMI~cancer_promoting_minus_preventing_FFQ  ,preprocessed_data)))

print(summary(lm(BMI~cancer_promoting_minus_preventing_FFQ+Gender3C +PSS_sum+
                    DEMO_Age+RaceCategorical ,preprocessed_data)))

print(summary(lm(BMI~cancer_promoting_minus_preventing_FFQ*Gender3C +PSS_sum+
                    DEMO_Age+RaceCategorical ,preprocessed_data)))
```
## Check: does food consumption mediate the relationship between rural status and higher BMI?

We'll focus on women since the relationship among women between FFQ and BMI in this sample is more straightforward.

```{r}

#https://www.rdocumentation.org/packages/mediation/versions/4.5.0/topics/mediate
library(mediation)

preprocessed_data_women <- preprocessed_data %>% filter(Gender3C=="Female")
#first need to only get rows that are NA on all the values; need to do this prior because we have two different models and need them using the same rows.
#strictly speaking, only need to add columns not included in both; lm package will consistently eliminate the rest.
exclude_row <- rowSums(is.na(preprocessed_data_women[,c("BMI","MESA_healthyfoodavailability")]))>0

#preprocessed_data_women$cancer_promoting_minus_preventing_FFQ <- log(preprocessed_data_women$cancer_promoting_minus_preventing_FFQ)
predict_mediator <- lm(cancer_promoting_minus_preventing_FFQ~RuralZIP+DEMO_Age+RaceCategorical,preprocessed_data_women[!exclude_row,])
predict_outcome <- lm(BMI~cancer_promoting_minus_preventing_FFQ+RuralZIP+DEMO_Age+RaceCategorical,preprocessed_data_women[!exclude_row,])

healthy_food_mediation <- mediate(predict_mediator,predict_outcome,boot=FALSE,sims=2000,treat="RuralZIP",mediator="cancer_promoting_minus_preventing_FFQ")
```

```{r}
summary(healthy_food_mediation)

```



```{r}

#https://www.rdocumentation.org/packages/mediation/versions/4.5.0/topics/mediate
library(mediation)

#preprocessed_data_women <- preprocessed_data %>% filter(Gender3C=="Female")
#first need to only get rows that are NA on all the values; need to do this prior because we have two different models and need them using the same rows.
#strictly speaking, only need to add columns not included in both; lm package will consistently eliminate the rest.
exclude_row <- rowSums(is.na(preprocessed_data[,c("BMI","MESA_healthyfoodavailability")]))>0

#preprocessed_data$cancer_promoting_minus_preventing_FFQ <- log(preprocessed_data$cancer_promoting_minus_preventing_FFQ)
predict_mediator <- lm(cancer_promoting_minus_preventing_FFQ~RuralZIP+DEMO_Age+RaceCategorical,preprocessed_data[!exclude_row,])
predict_outcome <- lm(BMI~cancer_promoting_minus_preventing_FFQ+RuralZIP+DEMO_Age+RaceCategorical,preprocessed_data[!exclude_row,])

healthy_food_mediation <- mediate(predict_mediator,predict_outcome,boot=FALSE,sims=2000,treat="RuralZIP",mediator="cancer_promoting_minus_preventing_FFQ")

summary(healthy_food_mediation)
```

## Full analysis from spreadsheet

So here, we're not looking at rural subjects in particular; we want to know about all subjects in general. How well can we explain FFQ and BMI from the attitude and lifestyle and environmental data?

https://docs.google.com/spreadsheets/d/1K1Ub8XsANENQo61p5b5UX2nG1RfJQiN4vqFewMaIWbA/edit?ouid=108542841632156028788&usp=sheets_home&ths=true

Our model is that there are three components contibuting to calorie intake:
 - environment (community and personal)
 - learned association between hunger nad unhealthy food (FCI-Crave)
 - Non-habitual preference for healthy food (FCI-like)
 
These influence FFQ.

FFQ in turn influences BMI, along with other factors like IPAQ.

So how well does this work out?

First let's test each of these alone.


#### Component 1: environment

```{r}
preprocessed_data$MESA_healthyfoodavailability_ln <- log(preprocessed_data$MESA_healthyfoodavailability)
```

```{r}

print(summary(lm(cancer_promoting_minus_preventing_FFQ~MESA_healthyfoodavailability+Gender3C +PSS_sum+DEMO_Age+RaceCategorical,preprocessed_data)))
print(summary(lm(cancer_promoting_minus_preventing_FFQ~MESA_healthyfoodavailability+MESA_safetyfromcrime+Gender3C +PSS_sum+DEMO_Age+RaceCategorical,preprocessed_data)))
print(summary(lm(cancer_promoting_minus_preventing_FFQ~MESA_healthyfoodavailability+MESA_neighborhoodconnectedness+MESA_safetyfromcrime+Gender3C +PSS_sum+DEMO_Age+RaceCategorical,preprocessed_data)))
```


So, healthy food availability is important, but the other community variables collected are marginal at best, and we'll leave them out.

#### Component 2: Craving/learned association


What about the next component: learned association betweeen hunger and food? Taking a lot of liberties, we approximate this as FCI-Crave

```{r}
print(summary(lm(cancer_promoting_minus_preventing_FFQ~FCI_cancer_promoting+FCI_craved_cancer_preventing+MESA_healthyfoodavailability+Gender3C +PSS_sum+DEMO_Age+RaceCategorical,preprocessed_data)))
```

Really interesting that age and PSS become significant AFTER adding these into the model! This is a good sign. I wonder if we should try looking at promote and prevent separately.



```{r}
print(summary(lm(cancer_promoting_FFQ~FCI_cancer_promoting+FCI_craved_cancer_preventing+MESA_healthyfoodavailability+Gender3C +PSS_sum+DEMO_Age+RaceCategorical,preprocessed_data)))

print(summary(lm(cancer_preventing_FFQ~FCI_cancer_promoting+FCI_craved_cancer_preventing+MESA_healthyfoodavailability+Gender3C +PSS_sum+DEMO_Age+RaceCategorical,preprocessed_data)))

```

Model really works bets on the prevention side. And with a gender split...


```{r}

print(summary(lm(cancer_promoting_minus_preventing_FFQ~FCI_cancer_promoting+FCI_craved_cancer_preventing+MESA_healthyfoodavailability +PSS_sum+DEMO_Age+RaceCategorical,preprocessed_data %>% filter(Gender3C=="Female"))))

print(summary(lm(cancer_promoting_FFQ~FCI_cancer_promoting+FCI_craved_cancer_preventing+MESA_healthyfoodavailability +PSS_sum+DEMO_Age+RaceCategorical,preprocessed_data %>% filter(Gender3C=="Female"))))

print(summary(lm(cancer_preventing_FFQ~FCI_cancer_promoting+FCI_craved_cancer_preventing+MESA_healthyfoodavailability +PSS_sum+DEMO_Age+RaceCategorical,preprocessed_data %>% filter(Gender3C=="Female"))))

```

Model still works best on the prevention side; but it doesn't improve over using the general model. So we'll stick with that.


#### Component 3: non-habit food preference



```{r}
print(summary(lm(cancer_promoting_minus_preventing_FFQ~FCI_cancer_promoting+FCI_craved_cancer_preventing+FCI_liked_cancer_preventing+FCI_liked_cancer_promoting+ MESA_healthyfoodavailability +PSS_sum+Gender3C+DEMO_Age+RaceCategorical,preprocessed_data)))


print(summary(lm(cancer_promoting_minus_preventing_FFQ~FCI_cancer_promoting+FCI_craved_cancer_preventing+FCI_liked_cancer_preventing+FCI_liked_cancer_promoting+ MESA_healthyfoodavailability +PSS_sum+DEMO_Age+RaceCategorical,preprocessed_data %>% filter(Gender3C=="Female"))))

```
Interesting! 
 - PSS no longer significant; seems to be explained by liked-cancer-preventing
 - FCI liked cancer promoting is insignificant generally
 - age no longer relevant once we include food preference in the model.
 - Compared to the first model where we included neither craving nor liking, Race has gone from relevant to not relevant at all.
 
 Overall we explain 36% of the variance among women, and 34% of variance in the all-gender model. This is not bad, really. Can we explain additional variance with any of the data we have?


IPAQ is not quite significant, but significant enoguh to include. But I'm not sure how to interpret this, considering we're still predicting food consumption.



```{r}

#preprocessed_data$household_income_per_person <- preprocessed_data$aSES_02/

print(summary(lm(cancer_promoting_minus_preventing_FFQ~FCI_cancer_promoting+FCI_craved_cancer_preventing+FCI_liked_cancer_preventing+FCI_liked_cancer_promoting+ MESA_healthyfoodavailability +PSS_sum+Gender3C+DEMO_Age+RaceCategorical+
                   aSES_01+aSES_02
                   ,preprocessed_data)))


print(summary(lm(cancer_promoting_minus_preventing_FFQ~FCI_cancer_promoting+FCI_craved_cancer_preventing+FCI_liked_cancer_preventing+FCI_liked_cancer_promoting+ MESA_healthyfoodavailability +PSS_sum+DEMO_Age+RaceCategorical+
                   aSES_01+aSES_02,preprocessed_data %>% filter(Gender3C=="Female"))))


```
So let's include household income....

Try marital status...
```{r}
preprocessed_data$marital_status <- factor(preprocessed_data$aSES_11)
```


```{r}

#preprocessed_data$household_income_per_person <- preprocessed_data$aSES_02/

print(summary(lm(cancer_promoting_minus_preventing_FFQ~FCI_cancer_promoting+FCI_craved_cancer_preventing+FCI_liked_cancer_preventing+FCI_liked_cancer_promoting+ MESA_healthyfoodavailability +PSS_sum+Gender3C+DEMO_Age+RaceCategorical+
                   aSES_02+marital_status
                   ,preprocessed_data)))


print(summary(lm(cancer_promoting_minus_preventing_FFQ~FCI_cancer_promoting+FCI_craved_cancer_preventing+FCI_liked_cancer_preventing+FCI_liked_cancer_promoting+ MESA_healthyfoodavailability +PSS_sum+DEMO_Age+RaceCategorical+
                   aSES_02+marital_status,preprocessed_data %>% filter(Gender3C=="Female"))))


```


No difference. hmm.

OK, that about does it. We still have the EDM and EAFH and perhaps some others. Some of these are psychological but I don't know how to theoretically include in the model.

Others are really outcomes. Still we should proceed with including them to see how much we can maximize our predictive power.

Or are we more interested in using a tree model or similar to try to optimally understand this data. 

I want tosee if we can do a bit more with social class. So we can include rurality, but also household income per person...

```{r}


print(summary(lm(cancer_promoting_minus_preventing_FFQ~FCI_cancer_promoting+FCI_craved_cancer_preventing+FCI_liked_cancer_preventing+FCI_liked_cancer_promoting+ MESA_healthyfoodavailability +PSS_sum+DEMO_Age+RaceCategorical+
                   aSES_02+RuralZIP,preprocessed_data %>% filter(Gender3C=="Female"))))


```
Let's get household income per person

```{r}
preprocessed_data$HouseholdIncomeBucket <- NA

preprocessed_data$HouseholdIncomeBucket[preprocessed_data$aSES_02==1]<-25000/2
preprocessed_data$HouseholdIncomeBucket[preprocessed_data$aSES_02==2]<-mean(c(25000,34999))
preprocessed_data$HouseholdIncomeBucket[preprocessed_data$aSES_02==3]<-mean(c(35000,49999))
preprocessed_data$HouseholdIncomeBucket[preprocessed_data$aSES_02==4]<-mean(c(50000,74999))
preprocessed_data$HouseholdIncomeBucket[preprocessed_data$aSES_02==5]<-mean(c(75000,99999))
preprocessed_data$HouseholdIncomeBucket[preprocessed_data$aSES_02==6]<-mean(c(100000,149999))
preprocessed_data$HouseholdIncomeBucket[preprocessed_data$aSES_02==7]<-150000


#gotta clean up the person column
preprocessed_data$aSES_03[preprocessed_data$aSES_03=="5    Sister  Niece  nephew  Friend  me"]<-5
preprocessed_data$aSES_03[preprocessed_data$aSES_03=="3 adults"]<-3
preprocessed_data$aSES_03[preprocessed_data$aSES_03=="2 kids,3 adults,"]<-5
preprocessed_data$aSES_03[preprocessed_data$aSES_03=="3 adults 1 child"]<-4
preprocessed_data$aSES_03[preprocessed_data$aSES_03=="four"]<-4
preprocessed_data$aSES_03[preprocessed_data$aSES_03=="40000"]<-NA
preprocessed_data$aSES_03<-as.numeric(preprocessed_data$aSES_03)
preprocessed_data$aSES_03[preprocessed_data$aSES_03==0]<-1
preprocessed_data$HouseholdIncomeBucketPerPerson <- preprocessed_data$HouseholdIncomeBucket/preprocessed_data$aSES_03
table(preprocessed_data$HouseholdIncomeBucketPerPerson)

```

```{r}

print(summary(lm(cancer_promoting_minus_preventing_FFQ~FCI_cancer_promoting+FCI_craved_cancer_preventing+FCI_liked_cancer_preventing+FCI_liked_cancer_promoting+ MESA_healthyfoodavailability +PSS_sum+Gender3C+DEMO_Age+RaceCategorical+
                   HouseholdIncomeBucketPerPerson
                   ,preprocessed_data)))


print(summary(lm(cancer_promoting_minus_preventing_FFQ~FCI_cancer_promoting+FCI_craved_cancer_preventing+FCI_liked_cancer_preventing+FCI_liked_cancer_promoting+ MESA_healthyfoodavailability +PSS_sum+DEMO_Age+RaceCategorical+
                   HouseholdIncomeBucketPerPerson,preprocessed_data %>% filter(Gender3C=="Female"))))


```

OK not going to include household income per person--works less well than straight household income.
How about other demo factors:ladder, education status


```{r}

print(summary(lm(cancer_promoting_minus_preventing_FFQ~FCI_cancer_promoting+FCI_craved_cancer_preventing+FCI_liked_cancer_preventing+FCI_liked_cancer_promoting+ MESA_healthyfoodavailability +PSS_sum+Gender3C+DEMO_Age+RaceCategorical+
                   aSES_02+DEMO_8+DEMO_4
                   ,preprocessed_data)))


print(summary(lm(cancer_promoting_minus_preventing_FFQ~FCI_cancer_promoting+FCI_craved_cancer_preventing+FCI_liked_cancer_preventing+FCI_liked_cancer_promoting+ MESA_healthyfoodavailability +PSS_sum+DEMO_Age+RaceCategorical+
                   aSES_02+DEMO_8+DEMO_4,
                 preprocessed_data %>% filter(Gender3C=="Female"))))
```
That's quite surprising!

OK. I think we've done all we can regarding demographics, and adding various features related to my model. Where does that leave us?

thinking about the way I'm modeling, I want interaction effects between my key variables:

 - FCI_craving
 - FCI_liking
 - MESA_food_availability
 
 

```{r}
#DV is - higher is less healthy
#MESA- higher is more healthy
#so cancer_promoting*Mesa predicting our DV should be positive
#cancer_reventing*Mesa predicting DV should be negative.
print(summary(lm(cancer_promoting_minus_preventing_FFQ~
                   FCI_cancer_promoting*MESA_healthyfoodavailability+
                   FCI_craved_cancer_preventing*MESA_healthyfoodavailability+
                   FCI_liked_cancer_preventing*MESA_healthyfoodavailability+
                   FCI_liked_cancer_promoting*MESA_healthyfoodavailability+
                   PSS_sum+Gender3C+DEMO_Age+RaceCategorical+
                   aSES_02+DEMO_8+DEMO_4
                   ,preprocessed_data)))


print(summary(lm(cancer_promoting_minus_preventing_FFQ~
                    FCI_cancer_promoting*MESA_healthyfoodavailability+
                   FCI_craved_cancer_preventing*MESA_healthyfoodavailability+
                   FCI_liked_cancer_preventing*MESA_healthyfoodavailability+
                   FCI_liked_cancer_promoting*MESA_healthyfoodavailability+
                   PSS_sum+DEMO_Age+RaceCategorical+
                   aSES_02+DEMO_8+DEMO_4,
                 preprocessed_data %>% filter(Gender3C=="Female"))))
```
 

## BMI

```{r}
print(summary(lm(BMI~FCI_cancer_promoting+FCI_craved_cancer_preventing+FCI_liked_cancer_preventing+FCI_liked_cancer_promoting+ MESA_healthyfoodavailability +PSS_sum+DEMO_Age+RaceCategorical+
                   aSES_02+RuralZIP + Gender3C,preprocessed_data)))


print(summary(lm(BMI~FCI_cancer_promoting+FCI_craved_cancer_preventing+FCI_liked_cancer_preventing+FCI_liked_cancer_promoting+ MESA_healthyfoodavailability +PSS_sum+DEMO_Age+RaceCategorical+
                   aSES_02+RuralZIP,preprocessed_data %>% filter(Gender3C=="Female"))))



```

## supplementary outcome measures

```{r}
print(summary(lm(BMI~FCI_cancer_promoting+FCI_craved_cancer_preventing+FCI_liked_cancer_preventing+FCI_liked_cancer_promoting+ MESA_healthyfoodavailability +PSS_sum+DEMO_Age+RaceCategorical+
                   aSES_02+RuralZIP + Gender3C+EAFH_fastfoodpast30days,preprocessed_data)))


print(summary(lm(BMI~FCI_cancer_promoting+FCI_craved_cancer_preventing+FCI_liked_cancer_preventing+FCI_liked_cancer_promoting+ MESA_healthyfoodavailability +PSS_sum+DEMO_Age+RaceCategorical+
                   aSES_02+RuralZIP+EAFH_fastfoodpast30days,preprocessed_data %>% filter(Gender3C=="Female"))))

```



## supplementary outcome measures

```{r}
print(summary(lm(BMI~FCI_cancer_promoting+FCI_craved_cancer_preventing+FCI_liked_cancer_preventing+FCI_liked_cancer_promoting+ MESA_healthyfoodavailability +PSS_sum+DEMO_Age+RaceCategorical+
                   aSES_02+RuralZIP + Gender3C+EAFH_fastfoodpast30days+EDM_forwardscore+EDM_reversescored,preprocessed_data)))


print(summary(lm(BMI~FCI_cancer_promoting+FCI_craved_cancer_preventing+FCI_liked_cancer_preventing+FCI_liked_cancer_promoting+ MESA_healthyfoodavailability +PSS_sum+DEMO_Age+RaceCategorical+
                   aSES_02+RuralZIP+EAFH_fastfoodpast30days+EDM_forwardscore+EDM_reversescored,preprocessed_data %>% filter(Gender3C=="Female"))))

```
```{r}
print(summary(lm(BMI~FCI_cancer_promoting+FCI_craved_cancer_preventing+FCI_liked_cancer_preventing+FCI_liked_cancer_promoting+ MESA_healthyfoodavailability +PSS_sum+DEMO_Age+RaceCategorical+
                   aSES_02+RuralZIP+EAFH_fastfoodpast30days+EDM_forwardscore+EDM_reversescored+FFQh_sum+AFSM+MESA_neighborhoodconnectedness+MESA_safetyfromcrime,preprocessed_data %>% filter(Gender3C=="Female"))))
```

Now take away predictors that seem really irrelevant

```{r}
print(summary(lm(BMI~FCI_cancer_promoting+FCI_craved_cancer_preventing+FCI_liked_cancer_preventing+FCI_liked_cancer_promoting+ MESA_healthyfoodavailability +DEMO_Age+RaceCategorical+
                   aSES_02+RuralZIP+EDM_reversescored+FFQh_sum,preprocessed_data %>% filter(Gender3C=="Female"))))
```

Hang on a moment! How come RuralZIP is no longer important

```{r}
print(summary(lm(BMI~FCI_cancer_promoting+FCI_craved_cancer_preventing+FCI_liked_cancer_preventing+FCI_liked_cancer_promoting+ MESA_healthyfoodavailability +DEMO_Age+RaceCategorical+
                   aSES_02+RuralZIP+EDM_reversescored+FFQh_sum,preprocessed_data %>% filter(Gender3C=="Female"))))
```

hmmm. There's some weird gender effect.

If we do the same model but include only men:


```{r}
print(summary(lm(BMI~FCI_cancer_promoting+FCI_craved_cancer_preventing+FCI_liked_cancer_preventing+FCI_liked_cancer_promoting+ MESA_healthyfoodavailability +DEMO_Age+RaceCategorical+
                   aSES_02+RuralZIP+EDM_reversescored+FFQh_sum,preprocessed_data %>% filter(Gender3C=="Male"))))
```

Are men driving the effect then? It's rural men vs. urban men?

Cutting it down to a simple model:


```{r}
 print(summary(lm(BMI~RuralZIP+MESA_healthyfoodavailability+DEMO_Age+Gender+RaceCategorical,preprocessed_data)))
```

```{r}
print(summary(lm(BMI~MESA_healthyfoodavailability+RuralZIP+DEMO_Age+RaceCategorical,preprocessed_data %>% filter(Gender3C=="Female"))))
print(summary(lm(BMI~MESA_healthyfoodavailability+RuralZIP+DEMO_Age+RaceCategorical,preprocessed_data %>% filter(Gender3C=="Male"))))
```

It's come back, below, by including the interaction of FFQ and gender.
```{r}
print(summary(lm(BMI~FFQ_cancer_promoting*Gender3C+ FFQ_cancer_preventing*Gender3C+FCI_craved_cancer_preventing+FCI_liked_cancer_preventing+FCI_liked_cancer_promoting+ MESA_healthyfoodavailability +PSS_sum+DEMO_Age+RaceCategorical+
                   aSES_02+RuralZIP+EAFH_fastfoodpast30days+EDM_forwardscore+EDM_reversescored+FFQh_sum+AFSM+MESA_neighborhoodconnectedness+MESA_safetyfromcrime,preprocessed_data)))
```

OK, so--the lesson here is that if we include all of the avilable data, there's a reasonably strong rural effect that we just can't explain away with ANY of the current measures we have here.


```{r}
print(summary(lm(BMI~FFQ_cancer_promoting*Gender3C+ FFQ_cancer_preventing*Gender3C+FCI_craved_cancer_preventing+FCI_liked_cancer_preventing+FCI_liked_cancer_promoting+ MESA_healthyfoodavailability +PSS_sum+DEMO_Age+I(DEMO_Age^2)+RaceCategorical+
                   aSES_02+RuralZIP+EAFH_fastfoodpast30days+EDM_forwardscore+EDM_reversescored+FFQh_sum+AFSM+MESA_neighborhoodconnectedness+MESA_safetyfromcrime,preprocessed_data)))
```





```{r}
print(summary(lm(BMI~FFQ_cancer_promoting*Gender3C+ FFQ_cancer_preventing*Gender3C+FCI_craved_cancer_preventing+FCI_liked_cancer_preventing+FCI_liked_cancer_promoting+ MESA_healthyfoodavailability +PSS_sum+DEMO_Age+I(DEMO_Age^2)+RaceCategorical+
                   aSES_02+RuralZIP+EAFH_fastfoodpast30days+EDM_forwardscore+EDM_reversescored+FFQh_sum+AFSM+MESA_neighborhoodconnectedness+MESA_safetyfromcrime,preprocessed_data)))
```


Trying that full model but only women:


```{r}
print(summary(lm(BMI~FFQ_cancer_promoting+ FFQ_cancer_preventing+FCI_craved_cancer_preventing+FCI_liked_cancer_preventing+FCI_liked_cancer_promoting+ MESA_healthyfoodavailability +PSS_sum+DEMO_Age+I(DEMO_Age^2)+RaceCategorical+
                   aSES_02+RuralZIP+EAFH_fastfoodpast30days+EDM_forwardscore+EDM_reversescored+FFQh_sum+AFSM+MESA_neighborhoodconnectedness+MESA_safetyfromcrime,
                 preprocessed_data %>% filter(Gender3C=="Female"))))
```

No effect at all.

And only men:



```{r}
print(summary(lm(BMI~FFQ_cancer_promoting+ FFQ_cancer_preventing+FCI_craved_cancer_preventing+FCI_liked_cancer_preventing+FCI_liked_cancer_promoting+ MESA_healthyfoodavailability +PSS_sum+DEMO_Age+I(DEMO_Age^2)+RaceCategorical+
                   aSES_02+RuralZIP+EAFH_fastfoodpast30days+EDM_forwardscore+EDM_reversescored+FFQh_sum+AFSM+MESA_neighborhoodconnectedness+MESA_safetyfromcrime,
                 preprocessed_data %>% filter(Gender3C=="Male"))))
```

```{r}
ggplot(preprocessed_data %>% filter(Gender3C %in% c("Male","Female")), aes(x=interaction(Gender3C,RuralZIP),y=BMI,group=interaction(RuralZIP,Gender3C), color=RuralZIP))+
  geom_boxplot()+geom_jitter()
```


Yep we have a big difference.

So:

 - Models with only women in them and a limit set of explanatory variables have a weak rurality effect
 - Models with only women in them and include the full set of variables I have available to me have no rurality effect at all
 - Models with only men in them and a limited set of explanatory variables have a strong rurality effect
 - Models with only men in them and include the full set of variables have an equally strong rurality effect.
 
In other words, our rural-urban divide is mainly in men, not in women, and the smaller divide that exists in women can be largely explained (or explained into non-significance) by including a variety of explanatory measures.


Perhaps we should follow-up with a further analysis aimed explicitly at explaining rural-urban divide in an exploratory way.

