---
title: "explore_orfcs_pilot_results"
author: "Ben Smith"
date: "10/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(dplyr)
```


we are primarily interested in ZIP code.

Get the results from pilot 1

```{r}
data_dir <- "/Users/benjaminsmith/Dropbox (University of Oregon)/UO-SAN Lab/Berkman Lab/Devaluation/analysis_files/data/"



pilot_1 <- readr::read_csv(paste0(data_dir, "cloudresearch_survey_results/Oregon Rural Food Consumption Survey Bespoke CR_October 18, 2021_11.34_pilot1.csv"))
pilot_2 <- readr::read_csv(paste0(data_dir, "cloudresearch_survey_results/ORFCS Bespoke CR2_October 18, 2021_11.31_pilot2.csv"))

complete_1 <- readr::read_csv(paste0(data_dir, "cloudresearch_survey_results/ORFCS Bespoke CR2_November 2, 2021_11.47.csv"))
```

The ZIP Code data is best used with the DEMO_6 field. Participants entered this one more than they did the one in address. But we should also check to see how many filled out address information.

```{r}

cols_to_extract <- c("aid","WEIGHT","HEIGHT_1","LocationLatitude","geo_lat","LocationLongitude","geo_lng", "AddressNum_1", "Address_1","Address_2", "Address_3","DEMO_6")
pilot_1_mergedata <- pilot_1[,cols_to_extract]
pilot_1_mergedata$survey <- "pilot1"
pilot_2_mergedata <- pilot_2[,cols_to_extract]
pilot_2_mergedata$survey <- "pilot2"

complete_1_mergedata <- complete_1[,cols_to_extract]
complete_1_mergedata$survey <- "complete1"

pilot_mergedata <- rbind(pilot_1_mergedata,pilot_2_mergedata) %>% rbind(complete_1_mergedata)

pilot_mergedata$PptZIPCode<-pilot_mergedata$DEMO_6
```

Based on `match_ppt_to_ruca_with_zip_code.Rmd`.


Now we want to get the RUCA codes.

```{r}
ruca2010_zip_code_descriptions <- readxl::read_xlsx(paste0(data_dir , "RUCA2010zipcode.xlsx" ),sheet = 1)
ruca2010_zip_codes <- readxl::read_xlsx(paste0(data_dir , "RUCA2010zipcode.xlsx" ),sheet = "Data")
ruca2010_zip_codes_details <- readxl::read_xlsx(paste0(data_dir , "RUCA2010zipcode.xlsx" ),sheet = "RUCA code description")
ruca1010_zip_code_ruca_description_table <- readr::read_csv(paste0(data_dir,"RUCA2010zipcode_primary_code_key.csv"))
```

Now, match the participant ZIP Codes to the RUCA 2010

```{r}
ppts_with_zip_ruca <- merge(pilot_mergedata,ruca2010_zip_codes,by.x="PptZIPCode",by.y="ZIP_CODE",all.x=TRUE,all.y=FALSE)
ppts_with_zip_ruca <- merge(ppts_with_zip_ruca,ruca1010_zip_code_ruca_description_table, by.x="RUCA1",by.y="PrimaryCode",all.x=TRUE,all.y=FALSE)
#View(ppts_with_zip_ruca)



```

The research objectives of the [grant](https://grants.nih.gov/grants/guide/rfa-files/RFA-CA-20-051.html) say:

> The purpose of this FOA is to solicit applications to develop, adapt, and test individual-, community- or multilevel interventions to address modifiable risk factors for cancer in rural populations, as defined by USDA Rural-Urban Continuum Codes (RUCC) 4-9, Rural-Urban Commuting Area (RUCA) codes 4-10, or Frontier and Remote (FAR) areas level 4.

So which subjects do we have at levels 4-10? Based on ZIP Code, we have

```{r}
ppts_with_zip_ruca$ClassifiedRural <- ppts_with_zip_ruca$RUCA1>=4
```

```{r}
ruca1010_zip_code_ruca_description_table
```
```{r}
table(ppts_with_zip_ruca$ClassifiedRural)
table(is.na(ppts_with_zip_ruca$ClassifiedRural))
```


```{r}
table(ppts_with_zip_ruca$Description,ppts_with_zip_ruca$ClassifiedRural)

```


HOw complete is the data?

```{r}
ppts_with_zip_ruca$provided_address <- !is.na(ppts_with_zip_ruca$Address_1) & !is.na(ppts_with_zip_ruca$AddressNum_1) & !is.na(ppts_with_zip_ruca$Address_2)
ppts_with_zip_ruca$provided_latlng <- !is.na(ppts_with_zip_ruca$geo_lat)
ppts_with_zip_ruca$provided_address_or_latlng <- ppts_with_zip_ruca$provided_address | ppts_with_zip_ruca$provided_latlng

table(ppts_with_zip_ruca$provided_address_or_latlng,ppts_with_zip_ruca$survey)

```


```{r}
table(ppts_with_zip_ruca$ClassifiedRural,ppts_with_zip_ruca$survey)
```


```{r}
table(ppts_with_zip_ruca$ClassifiedRural,ppts_with_zip_ruca$provided_address_or_latlng)
```

```{r}
chisq.test(ppts_with_zip_ruca$ClassifiedRural,ppts_with_zip_ruca$provided_address_or_latlng)
```



