---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

This notebook tracks the healthy environment paper where we present a pre-registered finding that having a healthier food environment is associated with lower BMIs, controlling for race, gender, and age.

We'll work across three datasets here: DEV, the ORFCS, and HINTS.

First, we need to do the pre-registered finding exactly as presented. It was for the ORFCS, so we need to load that first.

```{r}
library(stringr)
library(rstatix)
```

```{r}
library(magrittr)
library(dplyr)



data_dir <- "/Users/benjaminsmith/Dropbox (University of Oregon)/UO-SAN Lab/Berkman Lab/Devaluation/analysis_files/data/"

preprocessed_data_filepath <- paste0(data_dir,"cloudresearch_survey_results/orfcs_preprocessed_anon_by_subj.csv")
library(readr)
library(ggplot2)
library(GGally)
preprocessed_data_raw <- readr::read_csv(preprocessed_data_filepath)


rows_to_remove <- ((preprocessed_data_raw$EDM_forwardscore<2 & preprocessed_data_raw$EDM_reversescored>4) |
  (preprocessed_data_raw$EDM_forwardscore>=4.5 & preprocessed_data_raw$EDM_reversescored<2))
rows_to_remove[is.na(rows_to_remove)]<-FALSE
sum(rows_to_remove)
sub_ids_to_remove <- preprocessed_data_raw[rows_to_remove,"SID"]
preprocessed_data <- preprocessed_data_raw %>% filter((SID %in% unlist(sub_ids_to_remove))==FALSE)


preprocessed_data$DEMO_Age_c <- preprocessed_data$DEMO_Age-38 #using U.S. median age

preprocessed_data$RaceCategorical<-factor(preprocessed_data$RaceCategorical,levels=unique(preprocessed_data$RaceCategorical))

preprocessed_data$RuralZIP_i <- as.numeric(preprocessed_data$RuralZIP)
preprocessed_data$RaceCategorical2 <- as.character(preprocessed_data$RaceCategorical)
preprocessed_data$RaceCategorical2[preprocessed_data$RaceCategorical2=="RaceNotReported"] <- "OtherRaceRaceNotReported"
preprocessed_data$RaceCategorical2[preprocessed_data$RaceCategorical2=="OtherRace"] <- "OtherRaceRaceNotReported"
preprocessed_data$RaceCategorical2 <-factor(preprocessed_data$RaceCategorical2,levels=names(sort(table(preprocessed_data$RaceCategorical2),decreasing=TRUE)))

#need to remove this one data point for data quality issue.
preprocessed_data[!is.na(preprocessed_data$WEIGHT) & preprocessed_data$WEIGHT>500,c("WEIGHT","WEIGHT_kg","BMI")] <- NA
rm(preprocessed_data_raw)
orfcs_dataset<-preprocessed_data
```

```{r}
#put self-report items in z-score. It wont' change the estimate but it will make it easier to interpret
zscore <- function(x){
  return((x-mean(x,na.rm=TRUE))/sd(x,na.rm=TRUE))
}
```
### Load that DEV dataset


```{r}

dropbox_file_dir = "~/Dropbox (University of Oregon)/UO-SAN Lab/Berkman Lab/Devaluation/analysis_files/data/"

source("../dev_load_functions.R")

dev_data_by_ppt <- get_complete_data_by_ppt(dropbox_file_dir)
```


```{r}
dev_data_by_ppt %<>% 
  mutate(
    MESA_healthyfoodavailability_z =zscore(MESA_healthyfoodavailability),
    MESA_safetyfromcrime_z =zscore(MESA_safetyfromcrime),
    cancer_promoting_minus_preventing_FFQ_z = zscore(cancer_promoting_minus_preventing_FFQ),
    age365_c = age365 - mean(age365,na.rm=TRUE) #center age, but do not z-score it.
  )
```

### Right, now; what did we want to get out of the DEV dataset?

```{r}
predict_bmi <- lm(bmi~cancer_promoting_minus_preventing_FFQ_z+
                    age365_c+birthsex_factor+RaceCategorical,
                  dev_data_by_ppt)
summary(predict_bmi)

predict_bf_1 <- lm(bf_1~cancer_promoting_minus_preventing_FFQ_z+
                    age365_c+birthsex_factor+RaceCategorical,
                  dev_data_by_ppt)
summary(predict_bf_1)

```

While we can't confirm the relationship between BMI and FFQ in the DEV dataset, we do see a relationship between Body Fat Percentage and FFQ.

