---
title: "R Notebook"
output: html_notebook
---

```{r}
library(foreign)
library(stringr)
library(dplyr)
library(ggplot2)
```

```{r}
#hines_2020_raw<-read.spss(hines_location, use.value.label=TRUE,to.data.frame=TRUE)

hines_locations <- Sys.glob(file.path("/Users/benjaminsmith/Google Drive/oregon/data/protected_HINTS_data/","*/Hints_fda*.sav"))

raw_file_list <- vector(mode="list",length<-length(hines_locations))

for (i in 1:length(raw_file_list)){
  hines_filepath <- hines_locations[[i]]
  filename <- basename(hines_filepath)
  spss_rawfile <- read.spss(hines_filepath, use.value.label=TRUE,to.data.frame=TRUE)
  spss_rawfile[["filename"]] <- filename
  raw_file_list[[i]] <- spss_rawfile
}

```

```{r}

detect_key_cols <- function(spss_item){
    print(spss_item[["filename"]][[1]])
    print("Race_Cat2" %in% colnames(spss_item))
    print(paste0("PR_RUCA_2010", "PR_RUCA_2010" %in% colnames(spss_item)))
    print(paste0("RUC2013", "RUC2013" %in% colnames(spss_item)))
    
    print("Age" %in% colnames(spss_item))
    print("BMI" %in% colnames(spss_item))
}


#lapply(raw_file_list,detect_key_cols)
detect_key_cols(spss_rawfile)

```

So let's just join cycle 5, because all but one of cycle 4 have rural-urban zoning data, and none have RUCA.



To join these we need to do something about all these columns that are different. So let's find the intersection of columns that are in all items.

```{r}
shared_colnames <- colnames(raw_file_list[[1]])
for (i in 2:length(raw_file_list)){
  shared_colnames <- intersect(colnames(raw_file_list[[i]]),shared_colnames)
}

#we want a few eextra important columns of interest
cols_to_use <- c(shared_colnames,"Fruit","Vegetables")

#then trim each file back to just these shared columns.
#we've checked it will include the ones we want.
file_list_trimmed <- lapply(
  raw_file_list,
  function(cycle_5_df){
    return(cycle_5_df[intersect(cols_to_use,colnames(cycle_5_df))])
  }
  
)

```



```{r}
table(spss_rawfile$RUC2013)
HINTS_fda <- spss_rawfile
```
OK, so I don't think we need to tidy this up, we just need to use a bit of regex to process this into our boolean rural item.

```{r}

#preprocess
HINTS_fda$Age <- as.numeric(as.character(HINTS_fda$Age))
HINTS_fda$BMI <- as.numeric(as.character(HINTS_fda))

HINTS_fda$Age_c <- HINTS_fda$Age-38 #using U.S. median age
```
OK, we can't proceed with this because we have no measure of health outcome--not BMI or anything else.