---
title: "R Notebook"
output: html_notebook
---

```{r}
cwd<-getwd()

data_dir <- "/Users/bensmith/Dropbox (University of Oregon)/UO-SAN Lab/Berkman Lab/Devaluation/analysis_files/data/"

setwd(data_dir)

source("DEV2-RuralVsUrbanDataExam_R_2021-01-21_2323.r")

#setwd(cwd)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
```{r}
#let's use good old data.table, I miss it
library(data.table)
library(dplyr)

dev2_ru_dt_all_sessions<- data.table(data)

dev2_ru_session01 <- dev2_ru_dt_all_sessions[redcap_event_name %in% c("session_0_arm_1","t1_arm_1","session_1_arm_1")]



```

Let's get some participant information....

```{r}
ppt_id <- c("dev_id","date_0","address","birthsex","dob","race___1","race___2","race___3","race___4","race___5","race___6","race___7","race___8","age")
#only store info relevant to participant ID
participant_list_raw <- dev2_ru_session01[,ppt_id,with=FALSE]
#now remove missing data columns
blank_by_row <- rowSums(is.na(participant_list_raw))+rowSums(participant_list_raw=="",na.rm = TRUE)
#remove rows with the least amount of information
ppt_list_clean.1 <- participant_list_raw[blank_by_row<max(blank_by_row)]
ppt_list_clean <- ppt_list_clean.1[stringr::str_detect(ppt_list_clean.1$dev_id,"DEV\\d\\d\\d") & ppt_list_clean.1$dob!="",]

```


Great. Now let's get zipcodes for the participants


```{r}
#https://www.oreilly.com/library/view/regular-expressions-cookbook/9781449327453/ch04s14.html
ppt_list_clean$ZIPCode <- stringr::str_extract(trimws(ppt_list_clean$address),"[0-9]{5}(?:-[0-9]{4})?$")
#We have to remove participants where we didn't have addresses.
ppt_list_clean <- ppt_list_clean[!is.na(ppt_list_clean$address) & ppt_list_clean$address!=""]

#manually add a couple of zipcodes that were entered incorrectly but can be human-deduced
source(paste0(data_dir,"manual_tag_zipcodes.R"))

#remove entries where we really can't tag a zip, even manually.
ppt_list_clean <- ppt_list_clean[!is.na(ZIPCode)]

#remove address, and remove some tables we don't need anymore
ppt_list_clean$address <- NULL
rm(ppt_list_clean.1)
rm(participant_list_raw)
```

Useful:
https://mcdc.missouri.edu/applications/geocorr2014.html


```{r}
#this 
county_zip_table <- readr::read_csv(paste0(data_dir,"geocorr2014.csv"),skip = 1)# %>% filter(zipname=="Los Angeles, CA")
county_zip_table %>% filter (`County code`=="41039")
```

Let's take a look at the different county codes on offer.

```{r}
library(readxl)

rucc2013<-readxl::read_xls(paste0(data_dir,"ruralurbancodes2013.xls"),sheet="Rural-urban Continuum Code 2013")

rucc2013_codes_list <- rucc2013 %>% select(RUCC_2013,Description) %>% arrange(. , RUCC_2013) %>% unique
rucc2013_codes_list
```
```{r}
rucc_brief <- rucc2013 %>% select(FIPS,State,RUCC_2013)
```

Now we can code the ZIP codes with RUCC codes
```{r}
zip_to_rucc <- county_zip_table %>% select(`ZIP census tabulation area`,`County code`,`State abbreviation`) %>% merge(rucc_brief,by.x = "County code",by.y="FIPS")
zip_to_rucc$`ZIP census tabulation area` <- as.character(zip_to_rucc$`ZIP census tabulation area`) #store ZIP code as character to avoid confusion

```

```{r}
ppt_list_with_rucc <- merge(ppt_list_clean,data.table(zip_to_rucc),by.x="ZIPCode",by.y="ZIP census tabulation area",all.x=TRUE)
```

```{r}
table(ppt_list_with_rucc$RUCC_2013)
```

```{r}

```

