---
title: "Power analysis"
output: html_notebook
---

Measuring some correlations between values in order to estimate the number of qualtrics subjects we should have.

I'm interested in the following IVs:

 - Self Report Habit Index
 - Eating Dysregulation Measure
 - Food Craving Inventory [Healthy vs. Unehalthy food]
 - IPAQ
 
 and the following DVs:
 
  - BMI
  - Food Frequency Questionnaire
  

For FCI and FFQ we need to operationalize into healthy and unhealthy food.

```{r}
library(dplyr)
library(ggplot2)
library(rstatix)
load("~/Dropbox (University of Oregon)/UO-SAN Lab/Berkman Lab/Devaluation/analysis_files/data/scored_data.RData")

scored$score <- as.numeric(scored$score)
```

```{r}

#
scored %>% filter(scale_name %in% c("FCI")) %>% select(scored_scale) %>% unique

```
```{r}
scored$scale_name %>% unique
```


Now get BMI

```{r}
load("../../../files/data/ppt_list_w_data.RData")
ppt_bmi <- ppt_list_w_data %>% select(dev_id,bmi_0) %>% filter(!is.na(bmi_0))
rm(ppt_list_w_data)

```


```{r}

#iterate through each of our scales, and test their correlation with FCI and FFQ

#scales where there's a promote-prevent
promote_minus_prevent <- scored %>% 
  #filter for FFQ
  filter(scale_name %in% c("FFQ","FCI")) %>%
  #filter for the two cols we're interested in
  filter(scored_scale %in% c("cancer_promoting","cancer_preventing","craved_cancer_promoting","liked_cancer_promoting","craved_cancer_preventing","liked_cancer_preventing")) %>%
  #throw it out wide
  select(SID,scored_scale,score,survey_name,scale_name) %>% tidyr::pivot_wider(names_from = scored_scale,values_from = score) %>%
  #create a composite measure
  mutate("cancer_promoting_minus_preventing"=cancer_promoting-cancer_preventing,
         "cancer_promoting_minus_preventing_craved"=craved_cancer_promoting-craved_cancer_preventing,
         "cancer_promoting_minus_preventing_liked"=liked_cancer_promoting-liked_cancer_preventing
         ) %>%
  #wide across the surveys so that we can compare the surveys
  select(scale_name,survey_name,SID,cancer_promoting_minus_preventing,cancer_promoting_minus_preventing_craved,cancer_promoting_minus_preventing_liked) %>% 
  tidyr::pivot_wider(id_cols=c("SID","survey_name"),
                     names_from=scale_name,
                     values_from=c(
    "cancer_promoting_minus_preventing",
    "cancer_promoting_minus_preventing_craved",
    "cancer_promoting_minus_preventing_liked")
    )


single_scale_values <- scored %>% 
  #filter for FFQ
  filter(scale_name %in% c("EDM","PLAN","MESA_HealthyFood")) %>%
  #filter for the two cols we're interested in
  #filter(scored_scale %in% c("mean")) %>%#unnecessary
  #throw it out wide
  select(SID,scored_scale,score,survey_name,scale_name) %>% tidyr::pivot_wider(names_from = scored_scale,values_from = score) %>%
  #wide across the surveys so that we can compare the surveys
  select(scale_name,survey_name,SID,mean) %>% 
  tidyr::pivot_wider(id_cols=c("SID","survey_name"),
                     names_from=scale_name,
                     values_from=c("mean")
    )

#now merge these

scales_wide<-merge(promote_minus_prevent,single_scale_values,by=c("SID","survey_name"),all=TRUE)

ppt_data_wide <- merge(scales_wide,ppt_bmi,by.x="SID",by.y="dev_id",all=TRUE)

```


```{r}
IVs <- c("cancer_promoting_minus_preventing_craved_FCI","cancer_promoting_minus_preventing_liked_FCI","EDM","PLAN","MESA_HealthyFood")
DVs <- c("cancer_promoting_minus_preventing_FFQ","bmi_0")

#now we estimate R^2....
draw_names <- unique(ppt_data_wide$survey_name)

for (DV in DVs){
  for(IV in IVs){
    for (dn in draw_names){
      pairwise_not_na <- (is.na(ppt_data_wide %>% filter(survey_name==dn) %>% .[,IV])==FALSE) &  (is.na(ppt_data_wide %>% filter(survey_name==dn) %>% .[,DV])==FALSE)
      if(sum(pairwise_not_na)>0){
        print(paste0(DV,",", IV, " (",as.character(sum(pairwise_not_na)) , " values in ",dn,")"))
          cor_res <-cor.test(
            ppt_data_wide %>% filter(survey_name==dn) %>% .[,IV],
            ppt_data_wide %>% filter(survey_name==dn) %>% .[,DV],
            use = "complete.obs"
          )
          print(paste0("r value of ", as.character(cor_res$estimate)))
          

      }#else{
        #print(paste("no valid column pair for:",IV,",", DV, " (",dn,")"))
      #}
   }
  }
}




```


## Across-surveys

To do MESA, because it's in the ADOPT survey flow, we have to do it across surveys...

```{r}
IVs <- c("MESA_HealthyFood")
DVs <- c("cancer_promoting_minus_preventing_FFQ","bmi_0")

#now we estimate R^2....
draw_names <- unique(ppt_data_wide$survey_name)

for (DV in DVs){
  for(IV in IVs){
    for (dn_dv in draw_names){
      for (dn_iv in draw_names){
        dv_na <- (is.na(ppt_data_wide %>% filter(survey_name==dn_dv) %>% .[,DV])==FALSE)
        iv_na <- (is.na(ppt_data_wide %>% filter(survey_name==dn_iv) %>% .[,IV])==FALSE)
        
        iv_data <- ppt_data_wide %>% filter(survey_name==dn_iv) %>% .[,c("SID",IV)]
        dv_data <- ppt_data_wide %>% filter(survey_name==dn_dv) %>% .[,c("SID",DV)]
        dv_iv_data <- merge(iv_data,dv_data,on="sid",all = FALSE)
        pairwise_not_na <- sum(apply(is.na(dv_iv_data)==FALSE,1,all))
        if(pairwise_not_na>0){
          print(paste0(DV,"(",dn_dv,"),", IV, "(",dn_iv,") (",as.character(pairwise_not_na) , " values)"))
            cor_res <-cor.test(
              dv_iv_data[,IV],
              dv_iv_data[,DV],
              use = "complete.obs"
            )
            print(cor_res)
          #print(paste0("r value of ", as.character(cor_res$estimate)))
        }#else{
        #print(paste("no valid column pair for:",DV,"(",dn_dv,"),", IV, "(",dn_iv,")"))
      #}
      }
   }
  }
}




```


```{r}
library(ggplot2)


IVs <- c("MESA_HealthyFood")
DVs <- c("cancer_promoting_minus_preventing_FFQ","bmi_0")

#now we estimate R^2....
draw_names <- unique(ppt_data_wide$survey_name)


IV <- IVs[[1]]
DV <- DVs[[1]]

dn_dv<-"DEV Session 1 Surveys"
dn_iv<-"DEV ADOPT Survey Flow"


dv_na <- (is.na(ppt_data_wide %>% filter(survey_name==dn_dv) %>% .[,DV])==FALSE)
iv_na <- (is.na(ppt_data_wide %>% filter(survey_name==dn_iv) %>% .[,IV])==FALSE)

iv_data <- ppt_data_wide %>% filter(survey_name==dn_iv) %>% .[,c("SID",IV)]
dv_data <- ppt_data_wide %>% filter(survey_name==dn_dv) %>% .[,c("SID",DV)]
dv_iv_data <- merge(iv_data,dv_data,on="sid",all = FALSE)
contains_not_null <- any(apply(is.na(dv_iv_data)==FALSE,1,all))

print(paste0(DV,"(",dn_dv,"),", IV, "(",dn_iv,") (",as.character(nrow(dv_iv_data)) , " values)"))
  cor_res <-cor.test(
    dv_iv_data[,IV],
    dv_iv_data[,DV],
    use = "complete.obs"
  )
    print(cor_res)



ggplot(dv_iv_data,aes_string(x=IV,y=DV))+geom_point()
```



