---
title: "Replicate teh result in DEV"
output: html_notebook
---


```{r}
#install.packages("tidystats")
library(stringr)
library(dplyr)
library(ggplot2)
library(rstatix)

dropbox_file_dir = "~/Dropbox (University of Oregon)/UO-SAN Lab/Berkman Lab/Devaluation/analysis_files/data/"
```


```{r}
source("../dev_load_functions.R")

```


### test correlations, transform


```{r}
data_by_ppt <- get_complete_data_by_ppt(dropbox_file_dir)
```


#### outlier removal

https://www.active.com/fitness/calculators/bodyfat

Classification	Women (% Fat)	Men (% Fat)
Essential Fat	10-12%	2-4%
Athletes	14-20%	6-13%
Fitness	21-24%	14-17%
Acceptable	25-31%	18-25%
Obese	32% +	25% +



With ~200 subjects, how often would we expect subjects 2 or 3 or 4 SD outside the mean?

<!-- ```{r} -->
<!-- readr::write_csv(data_by_ppt, file = paste0(data_path,"data_by_ppt_environment_analysis.csv")) -->


<!-- ``` -->

### analysis replicating findings from the rural pop survey in dev


> To measure the effect of community on eating behavior and health, we will use two linear models to predict (1) eating behavior and (2) health outcome from
> (a) Community healthy food environment
> (b) Community safety
> (c) self-report confounding variables PSS-4
> (d) demographic confounders relating to age and race

First of all, let's look at hte relationship between [classical] FFQ and BMI:

```{r}
predict_bmi <- lm(bmi~cancer_promoting_minus_preventing_FFQ+
                    age365+birthsex_factor+RaceCategorical,
                  data_by_ppt)
summary(predict_bmi)

predict_bf_1 <- lm(bf_1~cancer_promoting_minus_preventing_FFQ+
                    age365+birthsex_factor+RaceCategorical,
                  data_by_ppt)
summary(predict_bf_1)


predict_bf_1 <- lm(bf_1~FFQ_fruit_and_vege+
                    age365+birthsex_factor+RaceCategorical,
                  data_by_ppt)
summary(predict_bf_1)

```


```{r}

predict_bmi <- lm(bmi~cancer_promoting_minus_preventing_FFQ+
                    age365+I(age365^2)+birthsex_factor+RaceCategorical,
                  data_by_ppt)
summary(predict_bmi)

predict_bf_1 <- lm(bf_1~cancer_promoting_minus_preventing_FFQ+
                    age365+I(age365^2)+birthsex_factor+RaceCategorical,
                  data_by_ppt)
summary(predict_bf_1)


predict_bf_1 <- lm(bf_1~FFQ_fruit_and_vege+
                    age365+I(age365^2)+birthsex_factor+RaceCategorical,
                  data_by_ppt)
summary(predict_bf_1)
```

OK, so BF% relates to FFQ, but we can't find any other relationship.






```{r}
predict_bmi <- lm(bmi~age365+RaceCategorical+MESA_healthyfoodavailability+MESA_safetyfromcrime,
                  data_by_ppt)
summary(predict_bmi)

predict_bf_1 <- lm(bf_1~age365+RaceCategorical+MESA_healthyfoodavailability+MESA_safetyfromcrime,
                  data_by_ppt)
summary(predict_bf_1)

predict_FFQ <- lm(cancer_promoting_minus_preventing_FFQ~age365+RaceCategorical+MESA_healthyfoodavailability+MESA_safetyfromcrime,
                  data_by_ppt)
summary(predict_FFQ)

```

What if we stretch out FFQ and MESA_healthyfoodavailability a bit?

```{r}
hist(data_by_ppt$MESA_healthyfoodavailability,breaks = 20)

invln <- function(x){
  x_invln <- log(max(x,na.rm = T)+1-x)
  new_top <- max(x_invln,na.rm=T)
  return(new_top-x_invln)
}
data_by_ppt$MESA_healthyfoodavailability_invln<-invln(data_by_ppt$MESA_healthyfoodavailability)
data_by_ppt$MESA_safetyfromcrime_invln<-invln(data_by_ppt$MESA_safetyfromcrime)
hist(data_by_ppt$MESA_healthyfoodavailability_invln,breaks = 20)
```




```{r}
predict_bmi <- lm(bmi~age365+RaceCategorical+MESA_healthyfoodavailability_invln+MESA_safetyfromcrime_invln,
                  data_by_ppt)
summary(predict_bmi)

predict_bf_1 <- lm(bf_1~age365+RaceCategorical+MESA_healthyfoodavailability_invln+MESA_safetyfromcrime_invln,
                  data_by_ppt)
summary(predict_bf_1)

predict_FFQ <- lm(cancer_promoting_minus_preventing_FFQ~age365+RaceCategorical+MESA_healthyfoodavailability_invln+MESA_safetyfromcrime_invln,
                  data_by_ppt)
summary(predict_FFQ)

```