---
title: "Rural environment Paper"
output:
  html_document:
    df_print: paged
---

This is a close look at the rurality, BMI, food availability mediation relationship:

 - How does it change when we add PSS_z?
 - How does it change when we change the racial categorization?
 - How does it change when we add `I(DEMO_age_c)`?


# Setup

```{r}
library(stringr)
library(rstatix)
library(foreign)
library(stringr)
library(dplyr)
library(ggplot2)
library(data.table)
```

## Setup the ORFCS dataset


```{r}
library(magrittr)
library(dplyr)



data_dir <- "/Users/benjaminsmith/Dropbox (University of Oregon)/UO-SAN Lab/Berkman Lab/Devaluation/analysis_files/data/"

preprocessed_data_filepath <- paste0(data_dir,"cloudresearch_survey_results/orfcs_preprocessed_anon_by_subj.csv")
library(readr)
library(ggplot2)
library(GGally)
preprocessed_data_raw <- readr::read_csv(preprocessed_data_filepath)


rows_to_remove <- ((preprocessed_data_raw$EDM_forwardscore<2 & preprocessed_data_raw$EDM_reversescored>4) |
  (preprocessed_data_raw$EDM_forwardscore>=4.5 & preprocessed_data_raw$EDM_reversescored<2))
rows_to_remove[is.na(rows_to_remove)]<-FALSE
sum(rows_to_remove)
sub_ids_to_remove <- preprocessed_data_raw[rows_to_remove,"SID"]
preprocessed_data <- preprocessed_data_raw %>% filter((SID %in% unlist(sub_ids_to_remove))==FALSE)
preprocessed_data$BMI_c <- preprocessed_data$BMI - mean(preprocessed_data$BMI,na.rm=TRUE)

preprocessed_data$DEMO_Age_c <- preprocessed_data$DEMO_Age-38 #using U.S. median age

preprocessed_data$RaceCategorical<-factor(preprocessed_data$RaceCategorical,levels=unique(preprocessed_data$RaceCategorical))

preprocessed_data$RuralZIP_i <- as.numeric(preprocessed_data$RuralZIP)
preprocessed_data$RaceC2 <- as.character(preprocessed_data$RaceCategorical)
preprocessed_data$RaceC2[preprocessed_data$RaceC2=="RaceNotReported"] <- "OtherRaceRaceNotReported"
preprocessed_data$RaceC2[preprocessed_data$RaceC2=="OtherRace"] <- "OtherRaceRaceNotReported"
preprocessed_data$RaceC2 <-factor(preprocessed_data$RaceC2,levels=names(sort(table(preprocessed_data$RaceC2),decreasing=TRUE)))
preprocessed_data$RaceC2 <- preprocessed_data$RaceC2

#need to remove this one data point for data quality issue.
preprocessed_data[!is.na(preprocessed_data$WEIGHT) & preprocessed_data$WEIGHT>500,c("WEIGHT","WEIGHT_kg","BMI")] <- NA
rm(preprocessed_data_raw)

zscore <- function(x){
  return((x-mean(x,na.rm=TRUE))/sd(x,na.rm=TRUE))
}

preprocessed_data$FFQ_fruits_ln_z <- as.numeric(preprocessed_data$FFQ_fruits) %>% log %>% zscore
preprocessed_data$FFQ_vegetables_ln_z <- as.numeric(preprocessed_data$FFQ_vegetables) %>% log %>% zscore
preprocessed_data$FFQ_fruit_vegetables_z <- (as.numeric(preprocessed_data$FFQ_fruits) + as.numeric(preprocessed_data$FFQ_vegetables)) %>% log %>% zscore



#11 is doctoral degree; 12+ are "other" and "decline to answer"
preprocessed_data$DEMO_4[preprocessed_data$DEMO_4>11]<-NA

preprocessed_data$Education_Categorical <- preprocessed_data$DEMO_4
preprocessed_data$Education_Categorical <- preprocessed_data$DEMO_4
preprocessed_data$Education_Categorical[preprocessed_data$DEMO_4<3] <- 3 #very few under three so we'll move them up
#very few over 9, so we move them down
preprocessed_data$Education_Categorical[preprocessed_data$DEMO_4>9] <- 9
#now add descriptors
preprocessed_data$Education_Categorical<-factor(
  preprocessed_data$Education_Categorical,
  levels=3:9,
  labels=c("No high school diploma",
           "High school diploma/GED",
           "Some college credit, no degree",
           "Trade, technical, or vocational training",
           "Associate's degree",
           "Bachelor's degree",
           "Master's, Professional, or doctoral degree")
)



orfcs_dataset<-preprocessed_data
```

```{r}
#put self-report items in z-score. It wont' change the estimate but it will make it easier to interpret

orfcs_dataset %<>% 
  mutate(
    MESA_healthyfoodavailability_z =zscore(MESA_healthyfoodavailability),
    MESA_safetyfromcrime_z =zscore(MESA_safetyfromcrime),
    PSS_z = zscore(PSS_sum),
    cancer_promoting_minus_preventing_FFQ_z = zscore(cancer_promoting_minus_preventing_FFQ),
    DEMO_Age_c = DEMO_Age - mean(DEMO_Age,na.rm=TRUE), #center age, but do not z-score it.
    aSES_02_z = zscore(aSES_02)
  )

```

```{r}
#https://www.rdocumentation.org/packages/mediation/versions/4.5.0/topics/mediate
library(mediation)
boot_times = 10000 # set this to 10000 for final analysis, and 100 for setting up
```

#Findings

## Pre-registered: A rural-urban BMI (and FFQ???) difference in Oregon, controlling for demographics


```{r}


predict_bmi_rural <- lm(BMI~RuralZIP+
                    #MESA_healthyfoodavailability+MESA_safetyfromcrime
                      PSS_z+
                    DEMO_Age_c+Gender3C+RaceC2,
                  orfcs_dataset)
summary(predict_bmi_rural)


```


How does this look when including the quadratic term for age?

```{r}
predict_bmi_rural <- lm(BMI~RuralZIP+
                    #MESA_healthyfoodavailability+MESA_safetyfromcrime
                      PSS_z+
                    DEMO_Age_c+I(DEMO_Age_c^2)+Gender3C+RaceC2,
                  orfcs_dataset)
summary(predict_bmi_rural)

```



## Pre-registered: food availability mediates BMI-rurality relationship

```{r}
hist(data_to_measure$MESA_healthyfoodavailability_z)
```


```{r}

library(mediation)

data_to_measure <- orfcs_dataset %>% filter(!is.na(BMI) & Gender3C %in% c("Male","Female"))

#Rurality -> Income -> BMI


mb <- lm(MESA_healthyfoodavailability_z~RuralZIP+Gender3C+DEMO_Age_c+RaceC2+PSS_z,data_to_measure)
mc <- lm(BMI~RuralZIP+Gender3C+DEMO_Age_c+RaceC2+MESA_healthyfoodavailability_z+PSS_z,data_to_measure)

mediate_result <- mediate(mb,mc,sims=boot_times, treat="RuralZIP",mediator="MESA_healthyfoodavailability_z")
summary(mediate_result)
```

### Using RobustSE instead


```{r}

library(mediation)

data_to_measure <- orfcs_dataset %>% filter(!is.na(BMI) & Gender3C %in% c("Male","Female"))

#Rurality -> Income -> BMI


mb <- lm(MESA_healthyfoodavailability_z~RuralZIP+Gender3C+DEMO_Age_c+RaceC2+PSS_z,data_to_measure)
mc <- lm(BMI~RuralZIP+Gender3C+DEMO_Age_c+RaceC2+MESA_healthyfoodavailability_z+PSS_z,data_to_measure)

mediate_result <- mediate(mb,mc,sims=boot_times, robustSE=TRUE, treat="RuralZIP",mediator="MESA_healthyfoodavailability_z")
summary(mediate_result)
```
### Using non-parametric bootstrap

Default is a quasi-Bayesian approximation for confidence intervals. If anything this will probably require more sims but it might be more robust. This is probably the preferred way to go...

```{r}

library(mediation)

data_to_measure <- orfcs_dataset %>% filter(!is.na(BMI) & Gender3C %in% c("Male","Female"))

#Rurality -> Income -> BMI


mb <- lm(MESA_healthyfoodavailability_z~RuralZIP_i+Gender3C+DEMO_Age_c+RaceC2+PSS_z,data_to_measure)
mc <- lm(BMI~RuralZIP_i+Gender3C+DEMO_Age_c+RaceC2+MESA_healthyfoodavailability_z+PSS_z,data_to_measure)

mediate_result <- mediate(mb,mc,sims=boot_times, boot=TRUE, treat="RuralZIP_i",mediator="MESA_healthyfoodavailability_z")
summary(mediate_result)
```
Still doesn't yield us the result we're looking for, though.

How much variation is there? 

### Repeating the above twice


```{r}

library(mediation)

data_to_measure <- orfcs_dataset %>% filter(!is.na(BMI) & Gender3C %in% c("Male","Female"))

#Rurality -> Income -> BMI


mb <- lm(MESA_healthyfoodavailability_z~RuralZIP_i+Gender3C+DEMO_Age_c+RaceC2+PSS_z,data_to_measure)
mc <- lm(BMI~RuralZIP_i+Gender3C+DEMO_Age_c+RaceC2+MESA_healthyfoodavailability_z+PSS_z,data_to_measure)

mediate_result <- mediate(mb,mc,sims=boot_times, boot=TRUE, treat="RuralZIP_i",mediator="MESA_healthyfoodavailability_z")
summary(mediate_result)
```


```{r}

library(mediation)

data_to_measure <- orfcs_dataset %>% filter(!is.na(BMI) & Gender3C %in% c("Male","Female"))

#Rurality -> Income -> BMI


mb <- lm(MESA_healthyfoodavailability_z~RuralZIP_i+Gender3C+DEMO_Age_c+RaceC2+PSS_z,data_to_measure)
mc <- lm(BMI~RuralZIP_i+Gender3C+DEMO_Age_c+RaceC2+MESA_healthyfoodavailability_z+PSS_z,data_to_measure)

mediate_result <- mediate(mb,mc,sims=boot_times, boot=TRUE, treat="RuralZIP_i",mediator="MESA_healthyfoodavailability_z")
summary(mediate_result)
```


### Use bias-corrected and accelerated confidence intervals

What if we used a different kind of boot CI type?
https://blog.methodsconsultants.com/posts/understanding-bootstrap-confidence-interval-output-from-the-r-boot-package/


```{r}

library(mediation)

data_to_measure <- orfcs_dataset %>% filter(!is.na(BMI) & Gender3C %in% c("Male","Female"))

#Rurality -> Income -> BMI


mb <- lm(MESA_healthyfoodavailability_z~RuralZIP_i+Gender3C+DEMO_Age_c+RaceC2+PSS_z,data_to_measure)
mc <- lm(BMI~RuralZIP_i+Gender3C+DEMO_Age_c+RaceC2+MESA_healthyfoodavailability_z+PSS_z,data_to_measure)

mediate_result <- mediate(mb,mc,sims=boot_times, boot=TRUE, boot.ci.type = "bca", treat="RuralZIP_i",mediator="MESA_healthyfoodavailability_z")
summary(mediate_result)
```



### adding quadratic term for age....

```{r}

library(mediation)

data_to_measure <- orfcs_dataset %>% filter(!is.na(BMI) & Gender3C %in% c("Male","Female"))

#Rurality -> Income -> BMI


mb <- lm(MESA_healthyfoodavailability_z~RuralZIP+Gender3C+DEMO_Age_c+I(DEMO_Age_c^2)+RaceC2+PSS_z,data_to_measure)
mc <- lm(BMI~RuralZIP+Gender3C+DEMO_Age_c+I(DEMO_Age_c^2)+RaceC2+MESA_healthyfoodavailability_z+PSS_z,data_to_measure)

mediate_result <- mediate(mb,mc,sims=boot_times, treat="RuralZIP",mediator="MESA_healthyfoodavailability_z")
summary(mediate_result)
```

### Removing the PSS_z



```{r}

library(mediation)

data_to_measure <- orfcs_dataset %>% filter(!is.na(BMI) & Gender3C %in% c("Male","Female"))

#Rurality -> Income -> BMI


mb <- lm(MESA_healthyfoodavailability_z~RuralZIP+Gender3C+DEMO_Age_c+RaceC2,data_to_measure)
mc <- lm(BMI~RuralZIP+Gender3C+DEMO_Age_c+RaceC2+MESA_healthyfoodavailability_z,data_to_measure)

mediate_result <- mediate(mb,mc,sims=boot_times, treat="RuralZIP",mediator="MESA_healthyfoodavailability_z")
summary(mediate_result)
```
This may be an improvement...

### using old Racial Categorization

```{r}

library(mediation)

data_to_measure <- orfcs_dataset %>% filter(!is.na(BMI) & Gender3C %in% c("Male","Female"))

#Rurality -> Income -> BMI


mb <- lm(MESA_healthyfoodavailability_z~RuralZIP+Gender3C+DEMO_Age_c+RaceCategorical+PSS_z,data_to_measure)
mc <- lm(BMI~RuralZIP+Gender3C+DEMO_Age_c+RaceCategorical+MESA_healthyfoodavailability_z+PSS_z,data_to_measure)

mediate_result <- mediate(mb,mc,sims=boot_times, treat="RuralZIP",mediator="MESA_healthyfoodavailability_z")
summary(mediate_result)
```

None of that really seems to make a difference--it's just luck of the draw. 