---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

To run this script:
1. Download HINTS 5 datasets from https://hints.cancer.gov/view-questions-topics/all-hints-questions.aspx to your data folder. Download all cycles of the data.
2. In the data folder, unzip each dataset.
3. Change the location parameter for the `get_hints5` call in the block below to point to your data folder.
4. Run this script.

```{r message=FALSE, warning=FALSE}
Sys.setenv(R_CONFIG_ACTIVE = Sys.info()["nodename"])

library(dplyr)
library(lavaan)
source("HINTS_preprocessing.R")
source("orfcs_utilities.R")
hints5 <-get_hints5(location=config::get("hints_protected_data_folderpath"))
boot_times<-50

zscore <- function(x){
    return((x-mean(x,na.rm=TRUE))/sd(x,na.rm=TRUE))
}
```


```{r}
# table(orfcs_dataset$RuralZIP_i,
#       orfcs_dataset$Gender3C,
#       orfcs_dataset$RaceCategorical=="HispanicAnyRace"
#       )
```


```{r}
sapply(c("Metropolitan", "Micropolitan", "Small town", "Rural"),
       function(cat){sum(grepl(cat,hints5$PR_RUCA_2010))}
       )
```


what's the variability between men and women

including exercise or energy expenditure

exercise can improve objective health without/before it changes BMI.

weight physical activity and food intake

low income women, particularly low income women head of households, are of particular concern, and possibly hispanic women

```{r}
#table(orfcs_dataset$RuralZIP_i,
#      orfcs_dataset$Gender3C,
#      orfcs_dataset$RaceCategorical=="HispanicAnyRace"
#      )
```

```{r}
table(hints5$GeneralHealth_of) %>% cumsum / sum(!is.na(hints5$GeneralHealth_of))

hist(as.integer(hints5$GeneralHealth_of))
```

```{r}
library(magrittr)
library(dplyr)



data_dir <- config::get("rural_data_dir")

preprocessed_data_filepath <- paste0(data_dir,"cloudresearch_survey_results/orfcs_preprocessed2_anon_by_subj.csv")
library(readr)
library(ggplot2)
library(GGally)
orfcs_dataset <- readr::read_csv(preprocessed_data_filepath)



```

Let's do our best to include all the same covariates we previously included.

# Prep

```{r}
library(stringi)
# [1] "Fruit_vegetables_z~HINTSIsRural_i+Age_c+I(Age_c^2)+RacePP+Gender3C+filename"
# [1] "MedConditions_HighBP_i~Fruit_vegetables_z+HINTSIsRural_i+Age_c+I(Age_c^2)+RacePP+Gender3C+filename"
# IncomeRanges_r

#need to do prepare variables so lavaan can process them
hints5_pp <- hints5
#add quadratic
hints5_pp$Age_c_pow2 <- hints5_pp$Age_c^2


#one-hot some variables
factor_to_clean_string <- function(data, col_to_stringify){
  data[[col_to_stringify]] <- as.character(data[[col_to_stringify]])
  data[[col_to_stringify]] <- (
    str_replace_all(data[[col_to_stringify]],"\\s","_") %>% 
      str_replace_all("\\W","")
  )#table(hints5_pp[[col_to_stringify]])
  return(data)
}

hints5_pp<-factor_to_clean_string(hints5_pp,"RacePP2")
hints5_pp$RacePP2<-factor(hints5_pp$RacePP2)
hints5_pp <- mltools::one_hot(hints5_pp,"RacePP2",dropCols = FALSE)
print(paste0(colnames(hints5_pp)[grepl("RacePP2_",colnames(hints5_pp))],collapse=" + "))

hints5_pp<-factor_to_clean_string(hints5_pp,"Hisp_Cat2")
hints5_pp$Hisp_Cat2<-factor(hints5_pp$Hisp_Cat2,levels=names(sort(table(hints5_pp$Hisp_Cat2),decreasing = TRUE)))
hints5_pp <- mltools::one_hot(hints5_pp,"Hisp_Cat2",dropCols = FALSE)
print(paste0(colnames(hints5_pp)[grepl("Hisp_Cat2_",colnames(hints5_pp))],collapse=" + "))

hints5_pp<-factor_to_clean_string(hints5_pp,"Gender3C")
hints5_pp$Gender3C<-factor(hints5_pp$Gender3C)
hints5_pp <- mltools::one_hot(hints5_pp,"Gender3C",dropCols = FALSE)
print(paste0(colnames(hints5_pp)[grepl("Gender3C_",colnames(hints5_pp))],collapse=" + "))



```

Now prepare the ORFCS dataset for lavaan.

```{r}
#need to do prepare variables so lavaan can process them
orfcs_dataset_pp <- data.table(orfcs_dataset)
#add quadratic
orfcs_dataset_pp$DEMO_Age_c_pow2 <- orfcs_dataset_pp$DEMO_Age_c^2


#one-hot some variables


orfcs_dataset_pp<-factor_to_clean_string(orfcs_dataset_pp,"RaceC2")
orfcs_dataset_pp$RaceC2<-factor(orfcs_dataset_pp$RaceC2)
orfcs_dataset_pp <- mltools::one_hot(orfcs_dataset_pp,"RaceC2",dropCols = FALSE)
print(paste0(colnames(orfcs_dataset_pp)[grepl("RaceC2_",colnames(orfcs_dataset_pp))],collapse=" + "))

orfcs_dataset_pp<-factor_to_clean_string(orfcs_dataset_pp,"Gender3C")
orfcs_dataset_pp$Gender3C<-factor(orfcs_dataset_pp$Gender3C)
orfcs_dataset_pp <- mltools::one_hot(orfcs_dataset_pp,"Gender3C",dropCols = FALSE)
print(paste0(colnames(orfcs_dataset_pp)[grepl("Gender3C_",colnames(orfcs_dataset_pp))],collapse=" + "))
```


# Oregon dataset: basic disparity


# HINTS dataset: two mediators

This follows Hayes PROCESS Model 6 with two mediators but we are doing it here in Lavaan.

Variables are:

-   Treatment: Rurality
-   Two Mediators: household income, and fruit and vegetable consumption, in that order.
-   Outcome: Physical and health measures. Altogether, we'll repeat the mediation several times, with the following outcomes variables: BMI, self-rated health, aggregated cardiometabolic health, and high blood pressure. (and cancer??)

This model below is adapted from <https://towardsdatascience.com/doing-and-reporting-a-serial-mediation-model-with-two-mediators-in-r-with-lavaan-739ed3155814>

I think they've left some things out. I need to do a bit more research to work out how to properly implement this, probably including a basic crash course in SEM.

For the basic HINTs lms, see `HINTS_health_outcomes.Rmd`.

```{r}
#TREAT=HINTSIsRural_i
#m1=IncomeRanges_r
#m2=Fruit_vegetables_z
#OUTCOME=MedConditions_HighBP_i


#NEXT TO DO: DEAL WITH CATEGORICAL DATA. GUIDE HERE: https://lavaan.ugent.be/tutorial/cat.html
hints_model_template=
"
  #Regressions
  IncomeRanges_r ~ ab*HINTSIsRural_i + Age_c + Age_c_pow2 + Gender3C_Male + Gender3C_MissingOrMultiple + RacePP2_American_Indian_or_Alaska_Native + RacePP2_Asian_Indian + RacePP2_Black + RacePP2_Chinese + RacePP2_Filipino + RacePP2_Japanese + RacePP2_Korean + RacePP2_Missing_Data + RacePP2_Multiple_races_selected + RacePP2_Other_Asian + RacePP2_Pacific_Islander + RacePP2_Vietnamese + Hisp_Cat2_Unknown + Hisp_Cat2_Mexican + Hisp_Cat2_Other_Hispanic + Hisp_Cat2_Puerto_Rican + Hisp_Cat2_Multiple_Hispanic_ethnicities_selected + Hisp_Cat2_Cuban
  
  Fruit_vegetables_z ~ bc*IncomeRanges_r + ac*HINTSIsRural_i + Age_c + Age_c_pow2 + Gender3C_Male + Gender3C_MissingOrMultiple + RacePP2_American_Indian_or_Alaska_Native + RacePP2_Asian_Indian + RacePP2_Black + RacePP2_Chinese + RacePP2_Filipino + RacePP2_Japanese + RacePP2_Korean + RacePP2_Missing_Data + RacePP2_Multiple_races_selected + RacePP2_Other_Asian + RacePP2_Pacific_Islander + RacePP2_Vietnamese + Hisp_Cat2_Unknown + Hisp_Cat2_Mexican + Hisp_Cat2_Other_Hispanic + Hisp_Cat2_Puerto_Rican + Hisp_Cat2_Multiple_Hispanic_ethnicities_selected + Hisp_Cat2_Cuban
  
  (OUTCOMEVAR) ~ cd*Fruit_vegetables_z + bd*IncomeRanges_r + ad*HINTSIsRural_i + Age_c + Age_c_pow2 + Gender3C_Male + Gender3C_MissingOrMultiple + RacePP2_American_Indian_or_Alaska_Native + RacePP2_Asian_Indian + RacePP2_Black + RacePP2_Chinese + RacePP2_Filipino + RacePP2_Japanese + RacePP2_Korean + RacePP2_Missing_Data + RacePP2_Multiple_races_selected + RacePP2_Other_Asian + RacePP2_Pacific_Islander + RacePP2_Vietnamese + Hisp_Cat2_Unknown + Hisp_Cat2_Mexican + Hisp_Cat2_Other_Hispanic + Hisp_Cat2_Puerto_Rican + Hisp_Cat2_Multiple_Hispanic_ethnicities_selected + Hisp_Cat2_Cuban
  
  
  #Defined Parameters:
  indirect_effect := ab*bc*cd
  effect_via_inc_only :=ab*bd
  effect_via_fruit_vege_only :=ac*cd
  direct_effect := ad
"

# - Outcome: Physical and health measures. Altogether, we'll repeat the mediation several times, with the following outcomes variables: BMI, self-rated health, aggregated cardiometabolic health, and high blood pressure.

outcome_measures <- c(
  "BMI",
  "GeneralHealth_i",
  "MedConditionsAggregate",
  "MedConditions_HighBP_i",
  "EverHadCancer_i"#no cancer for now, doesn't seem very important.
  )




```

```{r}



hints_fits_by_outcome<- list()

for (outcome_var in outcome_measures){
  set.seed(05711846)
  hints_model_w_outcome <- str_replace_all(hints_model_template,"\\(OUTCOMEVAR\\)",outcome_var)
  cat(paste0("MEDIATION MODEL FOR OUTCOME: ",outcome_var))
  cat(hints_model_w_outcome)
  fit=sem(
    hints_model_w_outcome,
    hints5_pp,
    se = "bootstrap",
    bootstrap=boot_times,
    likelihood = "wishart")
  
  hints_fits_by_outcome[[outcome_var]]<-fit
  summary(fit,ci=TRUE)
  cat("-----\n\n\n")
}
```



# HINTS dataset: removing hispanic regressors.

This follows Hayes PROCESS Model 6 with two mediators but we are doing it here in Lavaan.

Variables are:

-   Treatment: Rurality
-   Two Mediators: household income, and fruit and vegetable consumption, in that order.
-   Outcome: Physical and health measures. Altogether, we'll repeat the mediation several times, with the following outcomes variables: BMI, self-rated health, aggregated cardiometabolic health, and high blood pressure. (and cancer??)

This model below is adapted from <https://towardsdatascience.com/doing-and-reporting-a-serial-mediation-model-with-two-mediators-in-r-with-lavaan-739ed3155814>

I think they've left some things out. I need to do a bit more research to work out how to properly implement this, probably including a basic crash course in SEM.

For the basic HINTs lms, see `HINTS_health_outcomes.Rmd`.

```{r}
#TREAT=HINTSIsRural_i
#m1=IncomeRanges_r
#m2=Fruit_vegetables_z
#OUTCOME=MedConditions_HighBP_i


#NEXT TO DO: DEAL WITH CATEGORICAL DATA. GUIDE HERE: https://lavaan.ugent.be/tutorial/cat.html
hints_model_template=
"
  #Regressions
  IncomeRanges_r ~ ab*HINTSIsRural_i + Age_c + Age_c_pow2 + Gender3C_Male + Gender3C_MissingOrMultiple + RacePP2_American_Indian_or_Alaska_Native + RacePP2_Asian_Indian + RacePP2_Black + RacePP2_Chinese + RacePP2_Filipino + RacePP2_Japanese + RacePP2_Korean + RacePP2_Missing_Data + RacePP2_Multiple_races_selected + RacePP2_Other_Asian + RacePP2_Pacific_Islander + RacePP2_Vietnamese
  
  Fruit_vegetables_z ~ bc*IncomeRanges_r + ac*HINTSIsRural_i + Age_c + Age_c_pow2 + Gender3C_Male + Gender3C_MissingOrMultiple + RacePP2_American_Indian_or_Alaska_Native + RacePP2_Asian_Indian + RacePP2_Black + RacePP2_Chinese + RacePP2_Filipino + RacePP2_Japanese + RacePP2_Korean + RacePP2_Missing_Data + RacePP2_Multiple_races_selected + RacePP2_Other_Asian + RacePP2_Pacific_Islander + RacePP2_Vietnamese
  
  (OUTCOMEVAR) ~ cd*Fruit_vegetables_z + bd*IncomeRanges_r + ad*HINTSIsRural_i + Age_c + Age_c_pow2 + Gender3C_Male + Gender3C_MissingOrMultiple + RacePP2_American_Indian_or_Alaska_Native + RacePP2_Asian_Indian + RacePP2_Black + RacePP2_Chinese + RacePP2_Filipino + RacePP2_Japanese + RacePP2_Korean + RacePP2_Missing_Data + RacePP2_Multiple_races_selected + RacePP2_Other_Asian + RacePP2_Pacific_Islander + RacePP2_Vietnamese
  
  
  #Defined Parameters:
  indirect_effect := ab*bc*cd
  effect_via_inc_only :=ab*bd
  effect_via_fruit_vege_only :=ac*cd
  direct_effect := ad
"

# - Outcome: Physical and health measures. Altogether, we'll repeat the mediation several times, with the following outcomes variables: BMI, self-rated health, aggregated cardiometabolic health, and high blood pressure.

outcome_measures <- c(
  "BMI",
  "GeneralHealth_i",
  "MedConditionsAggregate",
  "MedConditions_HighBP_i",
  "EverHadCancer_i"#no cancer for now, doesn't seem very important.
  )




```

```{r}



hints_fits_by_outcome<- list()

for (outcome_var in outcome_measures){
  set.seed(05711846)
  hints_model_w_outcome <- str_replace_all(hints_model_template,"\\(OUTCOMEVAR\\)",outcome_var)
  cat(paste0("MEDIATION MODEL FOR OUTCOME: ",outcome_var))
  cat(hints_model_w_outcome)
  fit=sem(
    hints_model_w_outcome,
    hints5_pp,
    se = "bootstrap",
    bootstrap=boot_times,
    likelihood = "wishart")
  
  hints_fits_by_outcome[[outcome_var]]<-fit
  summary(fit,ci=TRUE)
  cat("-----\n\n\n")
}
```

## what's going wrong?
```{r}
lavInspect(fit,"cov.all")
```

# what if we take age^2 out?


```{r}
#TREAT=HINTSIsRural_i
#m1=IncomeRanges_r
#m2=Fruit_vegetables_z
#OUTCOME=MedConditions_HighBP_i


#NEXT TO DO: DEAL WITH CATEGORICAL DATA. GUIDE HERE: https://lavaan.ugent.be/tutorial/cat.html
hints_model_template=
"
  #Regressions
  IncomeRanges_r ~ ab*HINTSIsRural_i + Age_c + #Age_c_pow2 + 
  Gender3C_Male + Gender3C_MissingOrMultiple + RacePP2_American_Indian_or_Alaska_Native + RacePP2_Asian_Indian + RacePP2_Black + RacePP2_Chinese + RacePP2_Filipino + RacePP2_Japanese + RacePP2_Korean + RacePP2_Missing_Data + RacePP2_Multiple_races_selected + RacePP2_Other_Asian + RacePP2_Pacific_Islander + RacePP2_Vietnamese + Hisp_Cat2_Unknown + Hisp_Cat2_Mexican + Hisp_Cat2_Other_Hispanic + Hisp_Cat2_Puerto_Rican + Hisp_Cat2_Multiple_Hispanic_ethnicities_selected + Hisp_Cat2_Cuban
  
  Fruit_vegetables_z ~ bc*IncomeRanges_r + ac*HINTSIsRural_i + Age_c + #Age_c_pow2 + 
  Gender3C_Male + Gender3C_MissingOrMultiple + RacePP2_American_Indian_or_Alaska_Native + RacePP2_Asian_Indian + RacePP2_Black + RacePP2_Chinese + RacePP2_Filipino + RacePP2_Japanese + RacePP2_Korean + RacePP2_Missing_Data + RacePP2_Multiple_races_selected + RacePP2_Other_Asian + RacePP2_Pacific_Islander + RacePP2_Vietnamese + Hisp_Cat2_Unknown + Hisp_Cat2_Mexican + Hisp_Cat2_Other_Hispanic + Hisp_Cat2_Puerto_Rican + Hisp_Cat2_Multiple_Hispanic_ethnicities_selected + Hisp_Cat2_Cuban
  
  (OUTCOMEVAR) ~ cd*Fruit_vegetables_z + bd*IncomeRanges_r + ad*HINTSIsRural_i + Age_c + #Age_c_pow2 + 
  Gender3C_Male + Gender3C_MissingOrMultiple + RacePP2_American_Indian_or_Alaska_Native + RacePP2_Asian_Indian + RacePP2_Black + RacePP2_Chinese + RacePP2_Filipino + RacePP2_Japanese + RacePP2_Korean + RacePP2_Missing_Data + RacePP2_Multiple_races_selected + RacePP2_Other_Asian + RacePP2_Pacific_Islander + RacePP2_Vietnamese + Hisp_Cat2_Unknown + Hisp_Cat2_Mexican + Hisp_Cat2_Other_Hispanic + Hisp_Cat2_Puerto_Rican + Hisp_Cat2_Multiple_Hispanic_ethnicities_selected + Hisp_Cat2_Cuban
  
  
  #Defined Parameters:
  indirect_effect := ab*bc*cd
  effect_via_inc_only :=ab*bd
  effect_via_fruit_vege_only :=ac*cd
  direct_effect := ad
"

# - Outcome: Physical and health measures. Altogether, we'll repeat the mediation several times, with the following outcomes variables: BMI, self-rated health, aggregated cardiometabolic health, and high blood pressure.

outcome_measures <- c(
  "BMI",
  "GeneralHealth_i",
  "MedConditionsAggregate",
  "MedConditions_HighBP_i",
  "EverHadCancer_i"#no cancer for now, doesn't seem very important.
  )




```

```{r}



hints_fits_by_outcome<- list()

for (outcome_var in outcome_measures){
  set.seed(05711846)
  hints_model_w_outcome <- str_replace_all(hints_model_template,"\\(OUTCOMEVAR\\)",outcome_var)
  cat(paste0("MEDIATION MODEL FOR OUTCOME: ",outcome_var))
  cat(hints_model_w_outcome)
  fit=sem(
    hints_model_w_outcome,
    hints5_pp,
    se = "bootstrap",
    bootstrap=boot_times,
    likelihood = "wishart")
  
  hints_fits_by_outcome[[outcome_var]]<-fit
  summary(fit,ci=TRUE)
  cat("-----\n\n\n")
  break
}
```


```{r}
View(vcov(fit))
```

