---
title: "Rural environment Paper"
output:
  html_document:
    df_print: paged
---

We plan a paper on the rural environment, based on data here: https://docs.google.com/document/d/18f048q1x7UAKwgjXP7UNRuAT6Ad3XBXZHAi3dFYO2U4/edit#heading=h.n0uc8s3dggzu .


# Setup

```{r}
library(stringr)
library(rstatix)
library(foreign)
library(stringr)
library(dplyr)
library(ggplot2)
library(data.table)
```

Set directories

```{r}
Sys.setenv(R_CONFIG_ACTIVE = Sys.info()["nodename"])
data_dir <- config::get("rural_data_dir")
hints5_filepath <- config::get("hints_protected_data_folderpath")
```



# Original


```{r}
source("orfcs_utilities.R")
library(magrittr)
library(dplyr)


preprocessed_data_filepath <- paste0(data_dir,"cloudresearch_survey_results/orfcs_preprocessed2_anon_by_subj.csv")
#preprocessed_data_filepath <- paste0(config::get("orfcs_shareable_folder"),"oregon_dataset_anon.csv")

library(readr)
library(ggplot2)
library(GGally)
orfcs_dataset <- readr::read_csv(preprocessed_data_filepath)

#have to do this here because the file was saved in CSV, which converts factors to strings.
orfcs_dataset$Education_Categorical<-factor(
  orfcs_dataset$Education_Categorical,
  #levels=3:9,
  labels=c("No high school diploma",
           "High school diploma/GED",
           "Some college credit, no degree",
           "Trade, technical, or vocational training",
           "Associate's degree",
           "Bachelor's degree",
           "Master's, Professional, or doctoral degree")
)

orfcs_dataset$Education_Ordinal<-as.integer(orfcs_dataset$Education_Categorical)


```



```{r}
#orfcs_dataset %>% filter(is.na(BMI)) %>% dplyr::select(WEIGHT,HEIGHT_m) %>% is.na %>% colSums
orfcs_dataset %>% filter(!is.na(BMI) & !is.na(Gender3C) & !is.na(RuralZIP) & !is.na(PSS_z) & !is.na(DEMO_Age_c) & !is.na(Gender3C) & !is.na(RaceC2)) %>% .$RuralZIP %>% table
orfcs_dataset %>% filter(!is.na(cancer_promoting_minus_preventing_FFQ) & !is.na(Gender3C) & !is.na(RuralZIP) & !is.na(PSS_z) & !is.na(DEMO_Age_c) & !is.na(Gender3C) & !is.na(RaceC2)) %>% .$RuralZIP %>% table
predict_ffq_rural <- lm(cancer_promoting_minus_preventing_FFQ~RuralZIP+
                    #MESA_healthyfoodavailability+MESA_safetyfromcrime+
                      PSS_z+
                    DEMO_Age_c+Gender3C+RaceC2,
                  orfcs_dataset)
print(summary(predict_ffq_rural))
print(confint(predict_ffq_rural))

predict_bmi_rural <- lm(BMI~RuralZIP+
                    #MESA_healthyfoodavailability+MESA_safetyfromcrime
                      PSS_z+
                    DEMO_Age_c+Gender3C+RaceC2,
                  orfcs_dataset)
print(summary(predict_bmi_rural))
print(confint(predict_bmi_rural))

```



# Shareable




```{r}
source("orfcs_utilities.R")
library(magrittr)
library(dplyr)


preprocessed_data_filepath <- paste0(config::get("orfcs_shareable_folder"),"oregon_dataset_anon.csv")

library(readr)
library(ggplot2)
library(GGally)
orfcs_shareable <- readr::read_csv(preprocessed_data_filepath)

#have to do this here because the file was saved in CSV, which converts factors to strings.
orfcs_shareable$Education_Categorical<-factor(
  orfcs_shareable$Education_Categorical,
  #levels=3:9,
  labels=c("No high school diploma",
           "High school diploma/GED",
           "Some college credit, no degree",
           "Trade, technical, or vocational training",
           "Associate's degree",
           "Bachelor's degree",
           "Master's, Professional, or doctoral degree")
)

orfcs_shareable$Education_Ordinal<-as.integer(orfcs_shareable$Education_Categorical)

```



```{r}
#orfcs_dataset %>% filter(is.na(BMI)) %>% dplyr::select(WEIGHT,HEIGHT_m) %>% is.na %>% colSums
orfcs_shareable %>% filter(!is.na(BMI) & !is.na(Gender3C) & !is.na(RuralZIP) & !is.na(PSS_z) & !is.na(DEMO_Age_c) & !is.na(Gender3C) & !is.na(RaceC2)) %>% .$RuralZIP %>% table
orfcs_shareable %>% filter(!is.na(cancer_promoting_minus_preventing_FFQ) & !is.na(Gender3C) & !is.na(RuralZIP) & !is.na(PSS_z) & !is.na(DEMO_Age_c) & !is.na(Gender3C) & !is.na(RaceC2)) %>% .$RuralZIP %>% table
predict_ffq_rural <- lm(cancer_promoting_minus_preventing_FFQ~RuralZIP+
                      PSS_z+
                    DEMO_Age_c+Gender3C+RaceC2,
                  orfcs_shareable)
print(summary(predict_ffq_rural))
print(confint(predict_ffq_rural))

predict_bmi_rural <- lm(BMI~RuralZIP+
                      PSS_z+
                    DEMO_Age_c+Gender3C+RaceC2,
                  orfcs_shareable)
print(summary(predict_bmi_rural))
print(confint(predict_bmi_rural))



```


# Comparison

```{r}
orfcs_shareable[,c("BMI","RuralZIP","PSS_z","DEMO_Age_c","Gender3C","RaceC2")]
```



```{r}
orfcs_dataset[,c("BMI","RuralZIP","PSS_z","DEMO_Age_c","Gender3C","RaceC2")]
```
Right--which things are different between these datasets that create the small differences in outcomes and what do we do here?

```{r}
match_matrix <- orfcs_shareable[,c("BMI","RuralZIP","PSS_z","DEMO_Age_c","Gender3C","RaceC2")]==orfcs_dataset[,c("BMI","RuralZIP","PSS_z","DEMO_Age_c","Gender3C","RaceC2")]

print(colSums(match_matrix,na.rm = TRUE))
print(colSums(match_matrix==FALSE,na.rm = TRUE))


```

Okay, so--the BMI column is the only one containing differences. It's because I'm rounding BMI. Could I maybe round it to 0.1 instead of 1?

Let's take for example, one item
```{r}

round(60^2/175,1)

```

Let's go from BMI of 18 to a BMI of 35, increment by 0.3. How many different ways are there to get to each BMI point?

```{r}
bmi_combo_count_vec<-c()
for (target_bmi in (18+1:180*0.1)){
   target_bmi<-round(target_bmi,1) #get around floating point problems which occasionally arise.
   cat(target_bmi)

   #need to do this in feet & inches and pounds
   # HEIGHT_m =(HEIGHT_1*12+HEIGHT_2)*2.54/100,
   #  WEIGHT_kg = WEIGHT/2.20462
   ways_to_be_this_bmi_count<-0
   ways_to_be_this_bmi_str <- ""
   for (weight_lb in 90:400){
      for(height_inches in (4.5*12):(7*12)){
         weight_kg <- weight_lb/2.20462
         height_m <- height_inches*2.54/100
         
         
         #print(paste(weight_kg,height_m))
         #get a text string representing height in ft and inches
         height_ft_inches <- paste0(floor(height_inches/12), "'",round(height_inches %%12))
         bmi_rounded = round(weight_kg/height_m^2,1)
         
         if(bmi_rounded==target_bmi){
            ways_to_be_this_bmi_count=ways_to_be_this_bmi_count+1
            ways_to_be_this_bmi_str<-paste0(ways_to_be_this_bmi_str,weight_lb, ", ", height_ft_inches, " | ")
         }
         
      }
   }
   cat(paste0(": ",as.character(ways_to_be_this_bmi_count)," ways to be this BMI\n"))
   cat(ways_to_be_this_bmi_str)
   cat("\n")
   bmi_combo_count_vec = c(bmi_combo_count_vec, c(ways_to_be_this_bmi_count) )
}

```


```{r}
#demonstrating some floating point problems
which(round((18+1:180*0.1),1)==28.7)
which(as.character((18+1:180*0.1))==as.character(28.7))
```

```{r}
print(bmi_combo_count_vec)

```

OK so there are always lots of ways to be each of these BMIs, in combinations of feet and inches; therefore, we don't have to worry about denonymizing due to 1 d.p. rounded BMIs. Prefer to include them because the results will be close to that we obtained in the original analyses.