---
title: "R Notebook"
output: html_notebook
---

```{r message=FALSE, warning=FALSE}
library(dplyr)
library(lavaan)
source("HINTS_preprocessing.R")
hints5 <-get_hints5()
boot_times<-100

zscore <- function(x){
    return((x-mean(x,na.rm=TRUE))/sd(x,na.rm=TRUE))
}
```

```{r}
table(hints5$GeneralHealth_of) %>% cumsum / sum(!is.na(hints5$GeneralHealth_of))

hist(as.integer(hints5$GeneralHealth_of))
```


```{r}
library(magrittr)
library(dplyr)



data_dir <- "/Users/benjaminsmith/Dropbox (University of Oregon)/UO-SAN Lab/Berkman Lab/Devaluation/analysis_files/data/"

preprocessed_data_filepath <- paste0(data_dir,"cloudresearch_survey_results/orfcs_preprocessed2_anon_by_subj.csv")
library(readr)
library(ggplot2)
library(GGally)
orfcs_dataset <- readr::read_csv(preprocessed_data_filepath)



```


Let's do our best to include all the same covariates we previously included.

# HINTS dataset: two mediators

This follows Hayes PROCESS Model 6 with two mediators but we are doing it here in Lavaan.

Variables are:

 - Treatment: Rurality
 - Two Mediators: household income, and fruit and vegetable consumption, in that order.
 - Outcome: Physical and health measures. Altogether, we'll repeat the mediation several times, with the following outcomes variables: BMI, self-rated health, aggregated cardiometabolic health, and high blood pressure. (and cancer??)


This model below is adapted from https://towardsdatascience.com/doing-and-reporting-a-serial-mediation-model-with-two-mediators-in-r-with-lavaan-739ed3155814

I think they've left some things out. I need to do a bit more research to work out how to properly implement this, probably including a basic crash course in SEM.

```{r}
library(stringi)
# [1] "Fruit_vegetables_z~HINTSIsRural_i+Age_c+I(Age_c^2)+RacePP+Gender3C+filename"
# [1] "MedConditions_HighBP_i~Fruit_vegetables_z+HINTSIsRural_i+Age_c+I(Age_c^2)+RacePP+Gender3C+filename"
# IncomeRanges_r

#need to do prepare variables so lavaan can process them
hints5_pp <- hints5
#add quadratic
hints5_pp$Age_c_pow2 <- hints5_pp$Age_c^2


#one-hot some variables
factor_to_clean_string <- function(data, col_to_stringify){
  data[[col_to_stringify]] <- as.character(data[[col_to_stringify]])
  data[[col_to_stringify]] <- (
    str_replace_all(data[[col_to_stringify]],"\\s","_") %>% 
      str_replace_all("\\W","")
  )#table(hints5_pp[[col_to_stringify]])
  return(data)
}

hints5_pp<-factor_to_clean_string(hints5_pp,"RacePP2")
hints5_pp$RacePP2<-factor(hints5_pp$RacePP2)
hints5_pp <- mltools::one_hot(hints5_pp,"RacePP2",dropCols = FALSE)
print(paste0(colnames(hints5_pp)[grepl("RacePP2_",colnames(hints5_pp))],collapse=" + "))

hints5_pp<-factor_to_clean_string(hints5_pp,"Gender3C")
hints5_pp$Gender3C<-factor(hints5_pp$Gender3C)
hints5_pp <- mltools::one_hot(hints5_pp,"Gender3C",dropCols = FALSE)
print(paste0(colnames(hints5_pp)[grepl("Gender3C_",colnames(hints5_pp))],collapse=" + "))
```
Now prepare the ORFCS dataset for lavaan.


```{r}
#TREAT=HINTSIsRural_i
#m1=IncomeRanges_r
#m2=Fruit_vegetables_z
#OUTCOME=MedConditions_HighBP_i


#NEXT TO DO: DEAL WITH CATEGORICAL DATA. GUIDE HERE: https://lavaan.ugent.be/tutorial/cat.html
hints_model_test=
"
  #Regressions
  IncomeRanges_r ~ ab*HINTSIsRural_i + Age_c + Age_c_pow2 + Gender3C_Male + Gender3C_MissingOrMultiple + RacePP2_American_Indian_or_Alaska_Native + RacePP2_Asian_Indian + RacePP2_Black + RacePP2_Chinese + RacePP2_Filipino + RacePP2_Japanese + RacePP2_Korean + RacePP2_Missing_Data + RacePP2_Multiple_races_selected + RacePP2_Other_Asian + RacePP2_Pacific_Islander + RacePP2_Vietnamese
  
  Fruit_vegetables_z ~ bc*IncomeRanges_r + ac*HINTSIsRural_i + Age_c + Age_c_pow2 + Gender3C_Male + Gender3C_MissingOrMultiple + RacePP2_American_Indian_or_Alaska_Native + RacePP2_Asian_Indian + RacePP2_Black + RacePP2_Chinese + RacePP2_Filipino + RacePP2_Japanese + RacePP2_Korean + RacePP2_Missing_Data + RacePP2_Multiple_races_selected + RacePP2_Other_Asian + RacePP2_Pacific_Islander + RacePP2_Vietnamese
  
  EverHadCancer_i ~ cd*Fruit_vegetables_z + bd*IncomeRanges_r + ad*HINTSIsRural_i + Age_c + Age_c_pow2 + Gender3C_Male + Gender3C_MissingOrMultiple + RacePP2_American_Indian_or_Alaska_Native + RacePP2_Asian_Indian + RacePP2_Black + RacePP2_Chinese + RacePP2_Filipino + RacePP2_Japanese + RacePP2_Korean + RacePP2_Missing_Data + RacePP2_Multiple_races_selected + RacePP2_Other_Asian + RacePP2_Pacific_Islander + RacePP2_Vietnamese
  
  
  #Defined Parameters:
  indirect_effect := ab*bc*cd
  effect_via_inc_only :=ab*bd
  effect_via_fruit_vege_only :=ac*cd
  direct_effect := ad
  
"
fit=sem(
  hints_model_test,
  hints5_pp,
  se = "bootstrap",
  bootstrap=boot_times,
  likelihood = "wishart")

```

```{r}
PE_results <- summary(fit)$PE
```


```{r}
PE_results
```

```{r}
all_zscores <- PE_results$z
all_p_values <- PE_results$pvalue
```

```{r}
#calculate two-tailed -value
get_two_tailed_score <- function(z_score){
  return((1-pnorm(abs(z_score)))*2)
}
get_two_tailed_score(all_zscores)

```


