---
title: "Healthy environments are associated with lower BMIs controlling for race, gender, and age"
output:
  html_document:
    df_print: paged
---

This notebook tracks the healthy environment paper where we present a pre-registered finding that having a healthier food environment is associated with lower BMIs, controlling for race, gender, and age.

We'll work across two datasets here: DEV and ORFCS.

First, we need to do the pre-registered finding exactly as presented. It was for the ORFCS, so we need to load that first.

```{r}
library(stringr)
library(rstatix)
```

```{r}
library(magrittr)
library(dplyr)



data_dir <- "/Users/benjaminsmith/Dropbox (University of Oregon)/UO-SAN Lab/Berkman Lab/Devaluation/analysis_files/data/"

#preprocessed_data_filepath <- paste0(data_dir,"cloudresearch_survey_results/orfcs_preprocessed2_anon_by_subj.csv")
preprocessed_data_filepath <- paste0(config::get("orfcs_shareable_folder"),"oregon_dataset_anon.csv")
library(readr)
library(ggplot2)
library(GGally)
preprocessed_data <- readr::read_csv(preprocessed_data_filepath)


orfcs_dataset<-preprocessed_data
```

```{r}
#put self-report items in z-score. It wont' change the estimate but it will make it easier to interpret
zscore <- function(x){
  return((x-mean(x,na.rm=TRUE))/sd(x,na.rm=TRUE))
}
orfcs_dataset %<>% 
  mutate(
    MESA_healthyfoodavailability_z =zscore(MESA_healthyfoodavailability),
    MESA_safetyfromcrime_z =zscore(MESA_safetyfromcrime),
    PSS_z = zscore(PSS_sum),
    cancer_promoting_minus_preventing_FFQ_z = zscore(cancer_promoting_minus_preventing_FFQ),
    DEMO_Age_c = DEMO_Age - mean(DEMO_Age,na.rm=TRUE) #center age, but do not z-score it.
  )
```

```{r}
#https://www.rdocumentation.org/packages/mediation/versions/4.5.0/topics/mediate
library(mediation)
boot_times = 10000 # set this to 10000 for final analysis, and 100 for setting up
```

#Study 1

## Rurality and physical health outcomes


```{r}
#orfcs_dataset %>% filter(is.na(BMI)) %>% dplyr::select(WEIGHT,HEIGHT_m) %>% is.na %>% colSums
orfcs_dataset %>% filter(!is.na(BMI) & !is.na(Gender3C) & !is.na(RuralZIP) & !is.na(PSS_z) & !is.na(DEMO_Age_c) & !is.na(Gender3C) & !is.na(RaceC2)) %>% .$RuralZIP %>% table
orfcs_dataset %>% filter(!is.na(cancer_promoting_minus_preventing_FFQ) & !is.na(Gender3C) & !is.na(RuralZIP) & !is.na(PSS_z) & !is.na(DEMO_Age_c) & !is.na(Gender3C) & !is.na(RaceC2)) %>% .$RuralZIP %>% table
predict_ffq_rural <- lm(cancer_promoting_minus_preventing_FFQ~RuralZIP+
                    #MESA_healthyfoodavailability+MESA_safetyfromcrime+
                      PSS_z+
                    DEMO_Age_c+Gender3C+RaceC2,
                  orfcs_dataset)
print(summary(predict_ffq_rural))
print(confint(predict_ffq_rural))

predict_bmi_rural <- lm(BMI~RuralZIP+
                    #MESA_healthyfoodavailability+MESA_safetyfromcrime
                      PSS_z+
                    DEMO_Age_c+Gender3C+RaceC2,
                  orfcs_dataset)
print(summary(predict_bmi_rural))
print(confint(predict_bmi_rural))

```

## Mediators of the relation of rurality to health outcomes




```{r}


predict_bmi <- lm(BMI~
                    MESA_healthyfoodavailability_z+MESA_safetyfromcrime_z+PSS_z+
                    DEMO_Age_c+Gender3C+RaceC2,
                  orfcs_dataset)
summary(predict_bmi)
confint(predict_bmi)

predict_ffq <- lm(cancer_promoting_minus_preventing_FFQ_z~
                    MESA_healthyfoodavailability_z+MESA_safetyfromcrime_z+PSS_z+
                    DEMO_Age_c+Gender3C+RaceC2,
                  orfcs_dataset)
summary(predict_ffq)
confint(predict_ffq)
```

In each of these analyses, MESA_healthyfoodavailability is important, and is related to lower BMIs (b=-0.7, p<0.05) and FFQ (b=-0.07, p<0.001). That is, for every 1 SD in healthy food availability, we get -0.7 points on the BMI scale and -0.13 points on the z-scored Food Frequency Questionnaire.

We can also measures these while controlling for age as a quadratic variable:


```{r}


predict_bmi <- lm(BMI~
                    MESA_healthyfoodavailability_z+MESA_safetyfromcrime_z+PSS_z+
                    DEMO_Age_c+I(DEMO_Age_c^2)+Gender3C+RaceC2,
                  orfcs_dataset)
summary(predict_bmi)
confint(predict_bmi)

predict_ffq <- lm(cancer_promoting_minus_preventing_FFQ_z~
                    MESA_healthyfoodavailability_z+MESA_safetyfromcrime_z+PSS_z+
                    DEMO_Age_c+I(DEMO_Age_c^2)+Gender3C+RaceC2,
                  orfcs_dataset)
summary(predict_ffq)
confint(predict_ffq)
```

## Mediation




```{r mediation1_zip_food_availability}
set.seed(6472426)
library(mediation)

data_to_measure <- orfcs_dataset %>% filter(!is.na(BMI) & Gender3C %in% c("Male","Female"))

#Rurality -> Income -> BMI


mb <- lm(MESA_healthyfoodavailability_z~RuralZIP_i+Gender3C+DEMO_Age_c+RaceC2+PSS_z,data_to_measure)
mc <- lm(BMI~RuralZIP_i+Gender3C+DEMO_Age_c+RaceC2+MESA_healthyfoodavailability_z+PSS_z,data_to_measure)

mediate_result <- mediate(mb,mc,sims=boot_times, boot=TRUE,boot.ci.type = "bca", treat="RuralZIP_i",mediator="MESA_healthyfoodavailability_z")
summary(mediate_result)
summary(mc)
```


# Study 2

# Correlation matrix
